---
title: "docket_search (scotustext.R)"
author:
- name: Jake S. Truscott, Ph.D
  affiliation: University of Georgia
date: "`r Sys.Date()`"
output:
  html_document:
    css: gray.css
---


<style type="text/css">
  body{
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(scotustext)
library(tidyverse)
library(tidytext)
library(tm)
library(plyr)
library(textdata)
library(dplyr)
library(purrr)
library(tidyr)
library(ggplot2)
library(data.table)
library(ggrepel)
library(lubridate)
library(strex)
library(utils)
library(anytime)
library(zoo)
library(rvest)
library(webshot)
library(htmltools)
library(pdftools)
library(stringr)
library(htm2txt)
library(sjPlot)
library(reactable)
library(reactablefmtr)
library(httr)
library(devtools)

process_docket_id <- function(docket_id) {
  docket_url_newer <- "https://www.supremecourt.gov/search.aspx?filename=/docket/docketfiles/html/public/"
  docket_url_older <- "https://www.supremecourt.gov/search.aspx?filename=/docketfiles/"
  term <- as.data.frame(docket_id)
  term <- term %>%
    mutate(type = 3) %>%
    mutate(type = ifelse(grepl("m", docket_id, ignore.case = T), 2, type)) %>%
    mutate(type = ifelse(grepl("a", docket_id, ignore.case = T), 1, type)) %>%
    mutate(type = ifelse(grepl("o", docket_id, ignore.case = T), 4, type)) %>%
    mutate(year = as.numeric(gsub("\\-.*|a.*|A.*|m.*|M.*|Original.*|original.*|o.*|O.*|Orig.*|orig.*", "", docket_id))) %>%
    mutate(year = ifelse(as.numeric(year) %in% 0:9, as.character(paste0("0", year)), as.character(year))) %>%
    mutate(docket_number = gsub(".*\\-|.*a|.*A|.*m|.*M|.*Original|.*original|.*o|.*O|.*Orig|.*orig", "", docket_id)) %>%
    mutate(year = gsub("[^0-9]", "", year),
           docket_number = gsub("[^0-9]", "", docket_number)) %>% #Delete Non-Numbers
    mutate(html = ifelse(as.numeric(year) > 50, "HTM",
                         ifelse(as.numeric(year) < 17, "HTM",
                                ifelse(as.numeric(year) >= 17 & as.numeric(year) < 30, "HTML", "HTM")))) %>%
    mutate(url = case_when(
      type == 1 & html == "HTM" ~ paste0(docket_url_older, year, "a", docket_number, ".htm"),
      type == 1 & html == "HTML" ~ paste0(docket_url_newer, year, "a", docket_number, ".html"),

      type == 2 & html == "HTM" ~ paste0(docket_url_older, year, "m", docket_number, ".htm"),
      type == 2 & html == "HTML" ~ paste0(docket_url_newer, year, "m", docket_number, ".html"),

      type == 3 & html == "HTM" ~ paste0(docket_url_older, year, "-", docket_number, ".htm"),
      type == 3 & html == "HTML" ~ paste0(docket_url_newer, year, "-", docket_number, ".html"),

      type == 4 & html == "HTM" ~ paste0(docket_url_older, year, "o", docket_number, ".htm"),
      type == 4 & html == "HTML" ~ paste0(docket_url_newer, year, "o", docket_number, ".html")
    ))
  urls <- term$url
  return(urls)
}

clean_docket_frame <- function(docket_frame, include, exclude){

  {
    corpus <- tm::Corpus(VectorSource(docket_frame[["text"]]))
    corpus <- tm_map(corpus, content_transformer(gsub), pattern = "\\xe2\\x80\\xa2", replacement = " ")
    docket_entries <- data.frame(text = sapply(corpus, as.character), stringsAsFactors = FALSE) #Convert Corpus to Dataframe
    removeWordsWithBackslash <- function(inputString) {
      outputString <- gsub("\\S*\\\\\\\\\\S*\\s?", "", inputString)
      outputString <- iconv(outputString, "UTF-8", "ASCII", sub="")
      return(outputString)}
    docket_entries$text <- sapply(docket_entries$text, removeWordsWithBackslash)
  } #Base Clean (Corpus -> Toss "\\")
  {
    {
      docket_entries$docket_id <- docket_frame$url
      docket_entries$docket_url <- docket_frame$url
      docket_entries$docket_id <- gsub(".*(/Public/)", "", docket_entries$docket_id, ignore.case = TRUE)
      docket_entries$docket_id <- gsub(".*docketfiles\\/", "", docket_entries$docket_id )
      docket_entries$docket_id <- gsub(".html", "", docket_entries$docket_id)
      docket_entries$docket_id <- gsub(".htm", "", docket_entries$docket_id)
      docket_entries$docket_number <- docket_entries$docket_id
      docket_entries$text_original <- docket_entries$text
      docket_entries$metadata <- sub("PROCEEDINGS AND ORDERS.*", "", docket_entries$text_original, ignore.case = T)
      split_pr <- strsplit(docket_entries$metadata, "Docketed:")
      split_metadata <- strsplit(docket_entries$metadata, "\n")
      split_full <- strsplit(docket_entries$text_original, "\n")
    } #Initial Frame Process & Text Split
    {
      petitioner <- lapply(split_pr, function(row) {
        has_petitioner <- grepl("(Petitioner|Plaintiff|Petitioners|Plaintiffs|Appellant|Appellants|In Re|Applicant|Applicants)", row, ignore.case = TRUE)
        row[has_petitioner]
      })
      cleaned_petitioner <- lapply(petitioner, function(row) {
        row <- str_replace_all(row, "\n", " ")
        row <- str_replace_all(row, ".*Title:", "")
        row <- str_replace_all(row, "v\\..*", "")
        row <- str_replace_all(row, ", (Petitioner|Plaintiff|Petitioners|Plaintiffs|Appellant|Appellants|In Re|Applicant|Applicants).*", "")
        if (length(row) > 1) {
          row <- row[1]
        }

        row
      })
      nested_petitioner <- lapply(cleaned_petitioner, function(row) list(row))
      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", NA, x))
        return(modified_lst)
      }
      nested_petitioner <- replace_empty(nested_petitioner)
      docket_entries$petitioner <- sapply(nested_petitioner, function(x) paste(unlist(x), collapse = "; "))
      docket_entries$petitioner <- trimws(docket_entries$petitioner)


    } #Petitioner
    {
      respondent <- lapply(split_pr, function(row) {
        has_respondent <- grepl("(Petitioner|Plaintiff|Petitioners|Plaintiffs|Appellant|Appellants|In Re|Applicant|Applicants)", row, ignore.case = TRUE)
        row[has_respondent]
      })
      cleaned_respondent <- lapply(respondent, function(row) {
        row <- str_replace_all(row, "\n", "")
        row <- str_replace(row, ".*v\\.", "")
        if (length(row) > 1) {
          row <- row[1]
        }

        row
      })
      nested_respondent <- lapply(cleaned_respondent, function(row) list(row))
      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", NA, x))
        return(modified_lst)
      }
      nested_respondent <- replace_empty(nested_respondent)
      docket_entries$respondent <- sapply(nested_respondent, function(x) paste(unlist(x), collapse = "; "))
      docket_entries$respondent <- trimws(docket_entries$respondent)
      docket_entries$respondent = ifelse(grepl("In Re", docket_entries$petitioner, ignore.case = T), NA, docket_entries$respondent)

    } #Respondent
    {
      docketed <- lapply(split_metadata, function(row) {
        has_docketed <- grepl("Docketed:", row, ignore.case = TRUE)
        row[has_docketed]
      })
      cleaned_docketed <- lapply(docketed, function(row) {
        row <- str_replace_all(row, ".*Docketed: ", "")
        row <- trimws(row)
      })
      nested_docketed <- lapply(cleaned_docketed, function(row) list(row))
      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", NA, x))
        return(modified_lst)
      }
      nested_docketed <- replace_empty(nested_docketed)
      docket_entries$docketed <- sapply(nested_docketed, function(x) paste(unlist(x), collapse = "; "))
    } #Docketed
    {
      linked_with <- lapply(split_metadata, function(row) {
        has_linked_with <- grepl("Linked", row, ignore.case = TRUE)
        row[has_linked_with]
      })
      cleaned_linked_with <- lapply(linked_with, function(row) {
        row <- str_replace_all(row, ".*Linked with", "")
        row <- str_replace_all(row, "\\:", "")
        row <- trimws(row)
      })
      nested_linked_with <- lapply(cleaned_linked_with, function(row) list(row))
      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", NA, x))
        return(modified_lst)
      }
      nested_linked_with <- replace_empty(nested_linked_with)
      docket_entries$linked_with <- sapply(nested_linked_with, function(x) paste(unlist(x), collapse = "; "))
    } #Linked With
    {
      lower_court <- lapply(split_metadata, function(row) {
        has_lower_court <- grepl("Lower", row, ignore.case = TRUE)
        row[has_lower_court]
      })
      cleaned_lower_court <- lapply(lower_court, function(row) {
        row <- str_replace_all(row, ".*(Lower Ct: |Lower Court:)", "")
        row <- trimws(row)
      })
      nested_lower_court <- lapply(cleaned_lower_court, function(row) list(row))
      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", NA, x))
        return(modified_lst)
      }
      nested_lower_court <- replace_empty(nested_lower_court)
      docket_entries$lower_court <- sapply(nested_lower_court, function(x) paste(unlist(x), collapse = "; "))
    } #Lower Court
    {
      lower_court_case_number <- lapply(split_metadata, function(row) {
        has_lower_court_case_number <- grepl("(Case Number|Case Numbers|Case No)", row, ignore.case = TRUE)
        row[has_lower_court_case_number]
      })
      cleaned_lower_court_case_number <- lapply(lower_court_case_number, function(row) {
        row <- str_replace_all(row, ".*(Case Number: |Case Numbers: |Case No: )", "")
        row <- trimws(row)
      })
      nested_lower_court_case_number <- lapply(cleaned_lower_court_case_number, function(row) list(row))
      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", NA, x))
        return(modified_lst)
      }
      nested_lower_court_case_number <- replace_empty(nested_lower_court_case_number)
      docket_entries$lower_court_case_number <- sapply(nested_lower_court_case_number, function(x) paste(unlist(x), collapse = "; "))
    } #Lower Court Case Number
    {
      lower_court_decision_date <- lapply(split_metadata, function(row) {
        has_lower_court_decision_date <- grepl("Decision Date: ", row, ignore.case = TRUE)
        row[has_lower_court_decision_date]
      })
      cleaned_lower_court_decision_date <- lapply(lower_court_decision_date, function(row) {
        row <- str_replace_all(row, ".*(Decision Date:)", "")
        row <- trimws(row)
      })
      nested_lower_court_decision_date <- lapply(cleaned_lower_court_decision_date, function(row) list(row))
      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", NA, x))
        return(modified_lst)
      }
      nested_lower_court_decision_date <- replace_empty(nested_lower_court_decision_date)
      docket_entries$lower_court_decision_date <- sapply(nested_lower_court_decision_date, function(x) paste(unlist(x), collapse = "; "))
    } #Lower Court Case Number
    {
      docket_entries <- docket_entries %>%
        mutate(special_filing = ifelse(
          grepl("mandamus", text_original, ignore.case = T), "Mandamus", ifelse(grepl("habeas", text_original, ignore.case = T), "Habeas", ifelse(grepl("capital case", text_original, ignore.case = T), "Capital Case", ifelse(grepl("o", docket_number, ignore.case = T), "Original Jurisdiction", NA))))) %>%
        mutate(type = case_when(
          grepl("a", docket_number, ignore.case = T) ~ "Application",
          grepl("m", docket_number, ignore.case = T) ~ "Motion",
          grepl("-", docket_number, ignore.case = T) ~ "Docketed Case",
          grepl("o", docket_number, ignore.case = T) ~ "Docketed Case - Original Jurisdiction"
        )) %>%
        filter(!is.na(text_original)) %>%
        select(-c(text))

    } #Additional Terms

  } #Main Cleaning and Parsing
  {
    months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months) {
        original_text <- gsub(paste0("(\n)", month), paste0("\n###\n", month), original_text)
      }


      docket_entries$amicus_check[i] <- iconv(original_text, to = "UTF-8", sub = "")
      encoded_string <- docket_entries$amicus_check[i]

      split_rows <- strsplit(encoded_string, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_amicis_curiae_brief <- grepl("brief amici curiae|brief amicus curiae", row, ignore.case = TRUE)
        row[has_amicis_curiae_brief]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        row <- iconv(row, to = "UTF-8", sub = "")
        row <- str_remove(row, ".*amici curiae of |.*amicus curiae of ")
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        sub(" filed\\..*", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        str_remove(row, "\\nMain.*")
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        str_remove(row, "\\n")
      })
      nested_list <- lapply(cleaned_rows, function(row) list(row))

      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", "", x))
        return(modified_lst)
      }

      nested_list <- replace_empty(nested_list)


      docket_entries$amicus_filers[i] <- nested_list
      docket_entries <- docket_entries %>%
        mutate(amicus_filers = sapply(amicus_filers, function(x) paste(unlist(x), collapse = "; "))) %>%
        mutate(amicus_indicator = ifelse(amicus_filers == "", 0, 1)) %>%
        mutate(amicus_indicator = ifelse(is.na(amicus_filers), 0, amicus_indicator)) %>%
        mutate(amicus_count = sapply(docket_entries$amicus_filers, function(x) length(unlist(x)))) %>%
        mutate(amicus_count = ifelse(amicus_indicator == 0, 0, amicus_count))
    }
  } #Amicus Filings
  {
    months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months) {
        original_text <- gsub(paste0("(\n)", month), paste0("\n###\n", month), original_text)
      }

      docket_entries$argument_check[i] <- original_text
    }

    encoded_string <- docket_entries$argument_check
    split_rows <- strsplit(encoded_string, "\n###\n")
    filtered_rows <- lapply(split_rows, function(row) {
      has_argument <- grepl("Argued\\.", row, ignore.case = TRUE)
      row[has_argument]
    })
    cleaned_rows <- lapply(filtered_rows, function(row) {
      row <- iconv(row, to = "UTF-8", sub = "")
      row <- str_remove(row, " Argued\\..*")
    })
    nested_list <- lapply(cleaned_rows, function(row) paste(row, collapse = ", "))

    docket_entries$argument_date <- nested_list
    docket_entries <- docket_entries %>%
      mutate(argument_date = sapply(argument_date, function(x) paste(x, collapse = "; ")))


  } #Oral Argument Date
  {
    months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months) {
        original_text <- gsub(paste0("(\n)", month), paste0("\n###\n", month), original_text)
      }

      docket_entries$multiple_conference_check[i] <- original_text
    }

    split_rows <- strsplit(docket_entries$multiple_conference_check, "\n###\n")
    filtered_rows <- lapply(split_rows, function(row) {
      has_multiple_conference <- grepl("DISTRIBUTED for Conference", row, ignore.case = TRUE)
      row[has_multiple_conference]
    })
    cleaned_rows <- lapply(filtered_rows, function(row) {
      str_remove(row, ".*DISTRIBUTED for Conference of ")
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      gsub("\n\n.*", "", row)
      gsub("\n.*", "", row)
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      str_remove(row, "\\..*")
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      str_remove(row, "\n\n")
    })
    nested_list <- lapply(cleaned_rows, function(row) list(row))

    replace_empty <- function(lst) {
      modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", "", x))
      return(modified_lst)
    }

    nested_list <- replace_empty(nested_list)

    docket_entries$multiple_conference_dates <- nested_list
    docket_entries <- docket_entries %>%
      mutate(multiple_conference_dates = sapply(multiple_conference_dates, function(x) paste(unlist(x), collapse = "; "))) %>%
      mutate(conference_count = sapply(docket_entries$multiple_conference_dates, function(x) length(unlist(x))))

    docket_entries$first_conference_date <- sapply(docket_entries$multiple_conference_dates, function(x) {
      dates <- strsplit(x, "; ")[[1]]
      if (length(dates) > 0) {
        return(dates[1])
      } else {
        return("")
      }
    })


  } #Multiple Conference Dates
  {
    months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months) {
        original_text <- gsub(paste0("(\n)", month), paste0("\n###\n", month), original_text)
      }

      docket_entries$opinion_writer_check[i] <- original_text
    }

    split_rows <- strsplit(docket_entries$opinion_writer_check, "\n###\n")
    filtered_rows <- lapply(split_rows, function(row) {
      has_opinion_writer <- grepl("delivered the opinion", row, ignore.case = TRUE)
      row[has_opinion_writer]
    })
    cleaned_rows <- lapply(filtered_rows, function(row) {
      gsub("\n\n.*", "", row)
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      str_remove(row, " delivered the opinion.*")
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      gsub(", J\\.,", "", row)
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      gsub(", C\\. J\\.,", "", row)
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      str_remove(row, ".*\\. ")
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      str_remove(row, "\n\n")
    })
    nested_list <- lapply(cleaned_rows, function(row) paste(row, collapse = ", "))

    docket_entries$majority_opinion_writer <- nested_list

    docket_entries <- docket_entries %>%
      mutate(majority_opinion_writer = sapply(majority_opinion_writer, function(x) paste(x, collapse = "; "))) %>%
      mutate(majority_opinion_writer = ifelse(grepl("opinion per curiam", text_original, ignore.case = TRUE), "Per Curiam", majority_opinion_writer))

  } #Majority Opinion Writer
  {
    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months){
        original_text <- gsub(paste0("(\n)", month), paste0("\n###\n", month), original_text)
      }

      docket_entries$opinion_writer_check[i] <- original_text
    }

    split_rows <- strsplit(docket_entries$opinion_writer_check, "\n###\n")
    filtered_rows <- lapply(split_rows, function(row) {
      has_opinion_writer <- grepl("delivered the opinion", row, ignore.case = TRUE)
      row[has_opinion_writer]
    })
    cleaned_rows <- lapply(filtered_rows, function(row) {
      gsub("\n\n.*", "", row)
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      gsub(", J\\.,", "", row)
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      str_remove(row, "\n\n")
    })
    count_filed <- str_count(cleaned_rows, pattern = "filed")
    cleaned_rows <- str_count(cleaned_rows, pattern = "delivered") + count_filed

    docket_entries$number_of_opinions <- as.integer(cleaned_rows)
    docket_entries$number_of_opinions <- ifelse(grepl("per curiam", docket_entries$text_original, ignore.case = TRUE), "Per Curiam", docket_entries$number_of_opinions)

  } #Number of Opinions Filed
  {

    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months){
        original_text <- gsub(paste0("(\n)", month), paste0("\n###\n", month), original_text)
      }

      docket_entries$opinion_writer_check[i] <- original_text
    }

    split_rows <- strsplit(docket_entries$opinion_writer_check, "\n###\n")
    filtered_rows <- lapply(split_rows, function(row) {
      has_opinion_writer <- grepl("delivered the opinion", row, ignore.case = TRUE)
      row[has_opinion_writer]
    })
    cleaned_rows <- lapply(filtered_rows, function(row) {
      gsub("\n\n.*", "", row)
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      gsub(", J\\.,", "", row)
    })
    cleaned_rows <- lapply(cleaned_rows, function(row) {
      str_remove(row, "\n\n")
    })
    dissent_count <- sapply(cleaned_rows, function(row) {
      sum(grepl("dissent", row, ignore.case = TRUE))
    })
    concur_count <- sapply(cleaned_rows, function(row) {
      sum(grepl("concur", row, ignore.case = TRUE))
    })

    nested_filings <- lapply(seq_along(docket_entries$text_original), function(i) {
      list(
        dissent_count = paste0("Dissents: ", as.character(dissent_count[i])),
        concur_count = paste0("Concurrences: ", as.character(concur_count[i]))
      )
    })

    docket_entries$opinions_by_type <- nested_filings
    docket_entries <- docket_entries %>%
      mutate(opinions_by_type = sapply(opinions_by_type, function(x) paste(x, collapse = "; ")))



  } #Number of Opinions Filed (Breakdown)
  {
    months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months){
        original_text <- gsub(paste0("(\n)", month), paste0("\n###\n", month), original_text)
      }

      docket_entries$opinion_writer_check[i] <- original_text

      split_rows <- strsplit(docket_entries$opinion_writer_check[i], "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_opinion_writer <- grepl("delivered the opinion", row, ignore.case = TRUE)
        row[has_opinion_writer]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        gsub("\n\n.*", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(", J\\.,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        trimws(row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(", JJ\\.\\,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(", J\\.\\,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(", C\\. J\\.\\,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub("\\. ", "\n###\n", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        str_remove(row, "\n\n")
      })
      cleaned_rows <- unlist(cleaned_rows)
      split_rows <- strsplit(cleaned_rows, "\n###\n")

      contains_file_or_delivered <- function(row) {
        any(grepl("filed|delivered", row, ignore.case = TRUE))
      }

      split_rows <- lapply(split_rows, function(lst) {
        lst <- Filter(contains_file_or_delivered, lst)
        if (length(lst) > 0) {
          lst <- lst[!sapply(lst, is.null)]
        } else {
          lst <- ""
        }
        lst
      })

      docket_entries$opinion_filings[i] <- paste(unlist(split_rows), collapse = "; ")
    }
  } #Who Filed (And Joined)
  {
    docket_entries <- docket_entries %>%
      mutate(opinion_type = case_when(
        grepl("improvidently granted", text_original, ignore.case = TRUE) ~ "DIG",
        grepl("AFFIRMED", text_original, ignore.case = TRUE) ~ "AFFIRMED",
        grepl("Judgment VACATED and case REMANDED", text_original, ignore.case = TRUE) ~ "Vacated and Remanded",
        grepl("Judgments VACATED and cases REMANDED", text_original, ignore.case = TRUE) ~ "Vacated and Remanded",
        grepl("Judgment REVERSED and case REMANDED", text_original, ignore.case = TRUE) ~ "Reversed and Remanded",
        grepl("Judgments REVERSED and cases REMANDED", text_original, ignore.case = TRUE) ~ "Reversed and Remanded",
        grepl("REVERSED", text_original, ignore.case = TRUE) ~ "Reversed"
      )) %>%
      mutate(opinion_type = ifelse(is.na(opinion_type), "No Opinion Issued", opinion_type))

    months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months) {
        original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
      }

      docket_entries$gvr_check[i] <- iconv(original_text, to = "UTF-8", sub = "")
    }

    encoded_string <- docket_entries$gvr_check
    split_rows <- strsplit(encoded_string, "\n###\n")
    filtered_rows <- lapply(split_rows, function(row) {
      has_gvr_brief <- grepl("GRANTED", row, ignore.case = TRUE) &
        grepl("VACATED", row, ignore.case = TRUE) &
        grepl("REMANDED", row, ignore.case = TRUE)
      if (any(has_gvr_brief))
        "GVR"
      else
        row
    })

    docket_entries$gvr <- filtered_rows

    docket_entries <- docket_entries %>%
      mutate(opinion_type = ifelse(gvr == "GVR", "GVR", opinion_type))


  } #Type of Decision
  {
    {
      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]

        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }

        docket_entries$submitted_to_check[i] <- original_text
      }

      split_rows <- strsplit(docket_entries$submitted_to_check, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_submitted_to <- grepl("submitted to", row, ignore.case = TRUE)
        row[has_submitted_to]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        gsub("Justice ", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(".*submitted to ", "", row, ignore.case = T)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub("\\..*", "", row, ignore.case = T)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub("\\. ", "\n###\n", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        str_remove(row, "\n\n")
      })

      docket_entries$submitted_to <- cleaned_rows

      docket_entries <- docket_entries %>%
        mutate(submitted_to = sapply(submitted_to, paste, collapse = "; "))

      docket_entries$submitted_to <- ifelse(docket_entries$type == "Docketed Case", NA, docket_entries$submitted_to)
    } #Submitted To
    {
      docket_entries$referred_to_court <- ifelse(grepl("referred to the Court", docket_entries$text_original, ignore.case = T), "Yes", "No")
      docket_entries$referred_to_court <- ifelse(docket_entries$type == "Docketed Case", NA, docket_entries$referred_to_court)
    } #Referred to Court
    {
      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]

        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }

        docket_entries$application_type_check[i] <- original_text
      }

      split_rows <- strsplit(docket_entries$application_type_check, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_application_type <- grepl(", submitted to", row, ignore.case = TRUE)
        row[has_application_type]
      })

      cleaned_rows <- lapply(filtered_rows, function(row) {
        gsub("\\([^()]*\\)", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        trimws(row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(".*for ", "", row, ignore.case = )
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub("\\,.*", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub("a ", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        str_remove(row, "\n\n")
      })

      docket_entries$application_type = cleaned_rows
      docket_entries$application_type = ifelse(docket_entries$type == "Docketed Case", NA, docket_entries$application_type)
      docket_entries$application_type = str_to_title(docket_entries$application_type)


    } #Application Type



  } #Special Application Terms
  {
    {

      petitioner_pattern <- "(Attorneys for (Petitioner|Plaintiff|Petitioners|Plaintiff|Appellant|Appellants|Applicant|Applicants))\\n\\n([\\s\\S]*?)(?=\\n\\nAttorneys for (Respondent|Respondents|Appellee|Appellees)|(\\n|\\n\\n)Other|\\n\\n\\{1\\})"

      counsel <- docket_entries %>%
        select(text_original) %>%
        mutate(all_petitioner_counsel = str_extract_all(text_original, petitioner_pattern)) %>%
        mutate(all_respondent_counsel = str_extract(text_original, "(Attorneys for (Respondent|Respondents|Appellee|Appellees))\\n\\n([\\s\\S]*?)(?=(\\n\\n)|Other)")) %>%
        mutate(all_respondent_counsel = gsub("Attorneys for (Respondent|Respondents|Appellee|Appellees)", "", all_respondent_counsel)) %>%
        mutate(all_other_counsel = gsub("^.*Attorneys for (Respondent|Respondents|Appellee|Appellees)", "", text_original)) %>%
        mutate(all_other_counsel = gsub("\n\nOther", "<OTHER BREAK>", all_other_counsel)) %>%
        mutate(all_other_counsel = ifelse(grepl("<OTHER BREAK>", all_other_counsel),
                                          gsub(".*<OTHER BREAK>", "", all_other_counsel),
                                          ""))  %>%
        mutate(all_other_counsel = gsub("\n\n\\{1\\}", " <OTHER END> ", all_other_counsel)) %>%
        mutate(all_other_counsel = sub("<OTHER END>.*", "", all_other_counsel)) %>%
        mutate(all_respondent_counsel = gsub("\n", " <BREAK> ", all_respondent_counsel),
               all_petitioner_counsel = gsub("\n", " <BREAK> ", all_petitioner_counsel),
               all_other_counsel = gsub("\n", " <BREAK> ", all_other_counsel),) %>%
        mutate(all_respondent_counsel = gsub("(<BREAK>)(.*?Party.*?)(<BREAK>)", "\\1\\2 Attorney:\n\nAttorney:\\3", all_respondent_counsel, perl = TRUE),
               all_petitioner_counsel = gsub("(<BREAK>)(.*?Party.*?)(<BREAK>)", "\\1\\2 Attorney:\n\nAttorney:\\3", all_petitioner_counsel, perl = TRUE),
               all_other_counsel = gsub("(<BREAK>)(.*?Party.*?)(<BREAK>)", "\\1\\2 Attorney:\n\nAttorney:\\3", all_other_counsel, perl = TRUE)) %>%
        mutate(all_respondent_counsel = trimws(all_respondent_counsel),
               all_petitioner_counsel = trimws(all_petitioner_counsel),
               all_other_counsel = trimws(all_other_counsel))  %>%
        mutate(all_respondent_counsel = gsub("Attorneys for (Respondent|Respondents|Appellee|Appellees)", "\nAttorney:", all_respondent_counsel),
               all_petitioner_counsel = gsub("Attorneys for (Petitioner|Plaintiff|Petitioners|Plaintiff|Appellant|Appellants)", "\nAttorney:", all_petitioner_counsel)) %>%
        mutate(all_petitioner_counsel = gsub("Attorney: \\K<BREAK>\\s*<BREAK>", "", all_petitioner_counsel, perl = TRUE),
               all_respondent_counsel = gsub("Attorney: \\K<BREAK>\\s*<BREAK>", "", all_respondent_counsel, perl = TRUE),
               all_other_counsel = gsub("Attorney: \\K<BREAK>\\s*<BREAK>", "", all_other_counsel, perl = TRUE)) %>%
        mutate(all_respondent_counsel = gsub("<BREAK>", "\n", all_respondent_counsel),
               all_petitioner_counsel = gsub("<BREAK>", "\n", all_petitioner_counsel),
               all_other_counsel = gsub("<BREAK>", "\n", all_other_counsel)) %>%
        mutate(all_respondent_counsel = gsub("\nAttorney: \n", "\nAttorney:", all_respondent_counsel),
               all_petitioner_counsel = gsub("\nAttorney: \n", "\nAttorney:", all_petitioner_counsel),
               all_other_counsel = gsub("\nAttorney: \n", "\nAttorney:", all_other_counsel)) %>%
        mutate(all_respondent_counsel = gsub("Attorney:\n\n", "\n\n", all_respondent_counsel),
               all_petitioner_counsel = gsub("Attorney:\n\n", "\n\n", all_petitioner_counsel),
               all_other_counsel = gsub("Attorney:\n\n", "\n\n", all_other_counsel)) %>%
        mutate(all_respondent_counsel = gsub("\n\nAttorney:\n", "\n\n Attorney:", all_respondent_counsel),
               all_petitioner_counsel = gsub("Attorney:\n\n", "\n\n", all_petitioner_counsel),
               all_other_counsel = gsub("Attorney:\n\n", "\n\n", all_other_counsel)) %>%
        mutate(all_respondent_counsel = gsub("\nAttorney:", "Attorney:", all_respondent_counsel),
               all_petitioner_counsel = gsub("\nAttorney:", "Attorney:", all_petitioner_counsel),
               all_other_counsel = gsub("\nAttorney:", "Attorney:", all_other_counsel)) %>%
        mutate(all_respondent_counsel = gsub("Counsel of Record", "Organization:", all_respondent_counsel),
               all_petitioner_counsel = gsub("Counsel of Record", "Organization:", all_petitioner_counsel),
               all_other_counsel = gsub("Counsel of Record", "Organization:", all_other_counsel)) %>%
        mutate(all_petitioner_counsel = gsub("\\nAttorney:(.*)(\\nOrganization)", "\\nAttorney:\\1Organization", all_petitioner_counsel)) %>%
        mutate(all_respondent_counsel = trimws(all_respondent_counsel),
               all_petitioner_counsel = trimws(all_petitioner_counsel),
               all_other_counsel = trimws(all_other_counsel)) %>%
        mutate(all_respondent_counsel = gsub(" \n ", "\n", all_respondent_counsel),
               all_petitioner_counsel = gsub(" \n ", "\n", all_petitioner_counsel),
               all_other_counsel = gsub(" \n ", "\n", all_other_counsel)) %>%
        mutate(all_respondent_counsel = gsub(" \n\n ", "\n\n", all_respondent_counsel),
               all_petitioner_counsel = gsub(" \n\n ", "\n\n", all_petitioner_counsel),
               all_other_counsel = gsub(" \n\n ", "\n\n", all_other_counsel)) %>%
        mutate(all_petitioner_counsel = gsub(" {2}", " ", all_petitioner_counsel),
               all_respondent_counsel = gsub(" {2}", " ", all_respondent_counsel),
               all_other_counsel = gsub(" {2}", " ", all_other_counsel)) %>%
        mutate(all_petitioner_counsel = gsub("Attorney:\n", "\n\nAttorney:", all_petitioner_counsel),
               all_respondent_counsel = gsub("Attorney:\n", "\n\nAttorney:", all_respondent_counsel ),
               all_other_counsel = gsub("Attorney:\n", "\nAttorney:", all_other_counsel)) %>%
        mutate(all_respondent_counsel = ifelse(all_respondent_counsel != "" & !grepl("^Attorney:", all_respondent_counsel), paste0("Attorney: ", all_respondent_counsel), all_respondent_counsel),
               all_petitioner_counsel = ifelse(all_petitioner_counsel != "" & !grepl("^Attorney:", all_petitioner_counsel), paste0("Attorney: ", all_petitioner_counsel), all_petitioner_counsel),
               all_other_counsel = ifelse(all_other_counsel != "" & !grepl("^Attorney:", all_other_counsel), paste0("Attorney: ", all_other_counsel), all_other_counsel)) %>%
        mutate(contains_org_petitioner = !grepl("Organization", all_petitioner_counsel),
               contains_org_respondent = !grepl("Organization", all_respondent_counsel),
               contains_org_other = !grepl("Organization", all_other_counsel)) %>%
        mutate(all_petitioner_counsel = if_else(contains_org_petitioner, sub("\n", "\nOrganization: ", all_petitioner_counsel, fixed = TRUE), all_petitioner_counsel),
               all_respondent_counsel = if_else(contains_org_respondent, sub("\n", "\nOrganization: ", all_respondent_counsel, fixed = TRUE), all_respondent_counsel),
               all_other_counsel = if_else(contains_org_other, sub("\n", "\nOrganization: ", all_other_counsel, fixed = TRUE), all_other_counsel)) %>%
        mutate(all_petitioner_counsel = gsub("\n\nParty", "\nParty", all_petitioner_counsel),
               all_other_counsel = gsub("\n\nParty", "\nParty", all_other_counsel),
               all_respondent_counsel = gsub("\n\nParty", "\nParty", all_respondent_counsel))




    } #Parsing Counsel
    {
      extract_info <- function(record) {
        lines <- strsplit(record, "\n")[[1]]
        info <- list()

        for (line in lines) {
          if (grepl("^Attorney:", line)) {
            if (!exists("Attorney", info))
              info$Attorney <- list()
            info$Attorney <- c(info$Attorney, gsub("^Attorney: ", "", line))
          } else if (grepl("^Organization:", line)) {
            if (!exists("Organization", info))
              info$Organization <- list()
            info$Organization <- c(info$Organization, gsub("^Organization: ", "", line))
          } else if (grepl("^Party name:", line)) {
            if (!exists("PartyName", info))
              info$PartyName <- list()
            info$PartyName <- c(info$PartyName, gsub("^Party name: ", "", line))
          }
        }

        return(info)
      }


      {
        if (is.na(counsel$all_petitioner_counsel) || counsel$all_petitioner_counsel == "") {
          records_petitioner <- NA
        } else {
          records_petitioner <- lapply(counsel$all_petitioner_counsel, function(x) {
            flattened <- unlist(strsplit(x, "\n\n"))
            flattened <- lapply(flattened, function(x) {
              if (grepl("Organization:(.*)\\nParty name:", x, perl = TRUE)) {
                x <- gsub("Organization:(.*)\\nParty name:", "Organization:\\1\nParty name:", x, perl = TRUE)
              }
              x <- gsub("\n(?!\\n)", " ", x, perl = TRUE)
              trimws(x)
              x <- gsub(" Organization:", " \nOrganization:", x)
              x <- gsub(" Party name:", " \nParty name:", x)
            })
            paste(flattened, collapse = "; ")
          })
        }
        docket_entries$all_petitioner_counsel <- records_petitioner

      } #Petitioner Counsel

      {
        if (is.na(counsel$all_respondent_counsel) || counsel$all_respondent_counsel == "") {
          records_respondent <- NA
        } else {
          records_respondent <- lapply(counsel$all_respondent_counsel, function(x) {
            flattened <- unlist(strsplit(x, "\n\n"))
            flattened <- lapply(flattened, function(x) {
              if (grepl("Organization:(.*)\\nParty name:", x, perl = TRUE)) {
                x <- gsub("Organization:(.*)\\nParty name:", "Organization:\\1\nParty name:", x, perl = TRUE)
              }
              x <- gsub("\n(?!\\n)", " ", x, perl = TRUE)
              trimws(x)
              x <- gsub(" Organization:", " \nOrganization:", x)
              x <- gsub(" Party name:", " \nParty name:", x)
            })
            paste(flattened, collapse = "; ")
          })
        }
        docket_entries$all_respondent_counsel <- records_respondent

      } #Respondent Counsel

      {
        if (is.na(counsel$all_other_counsel) || counsel$all_other_counsel == "") {
          records_other <- NA
        } else {
          records_other <- lapply(counsel$all_other_counsel, function(x) {
            flattened <- unlist(strsplit(x, "\n\n"))
            flattened <- lapply(flattened, function(x) {
              if (grepl("Organization:(.*)\\nParty name:", x, perl = TRUE)) {
                x <- gsub("Organization:(.*)\\nParty name:", "Organization:\\1\nParty name:", x, perl = TRUE)
              }
              x <- gsub("\n(?!\\n)", " ", x, perl = TRUE)
              trimws(x)
              x <- gsub(" Organization:", " \nOrganization:", x)
              x <- gsub(" Party name:", " \nParty name:", x)
            })
            paste(flattened, collapse = "; ")
          })
        }
        docket_entries$all_other_counsel <- records_other

      } #Other Counsel

      docket_entries <- docket_entries %>%
        mutate(petitioner_counsel = gsub("\\;.*", "", all_petitioner_counsel),
               respondent_counsel = gsub("\\;.*", "", all_respondent_counsel)) %>%
        mutate(petitioner_counsel = gsub(".*Attorney: ", "", petitioner_counsel),
               respondent_counsel = gsub(".*Attorney: ", "", respondent_counsel)) %>%
        mutate(petitioner_counsel = trimws(petitioner_counsel),
               respondent_counsel = trimws(respondent_counsel)) %>%
        mutate(petitioner_counsel = gsub("(?:\\s{3}.*)?$", "", petitioner_counsel, perl = TRUE),
               respondent_counsel = gsub("(?:\\s{3}.*)?$", "", respondent_counsel , perl = TRUE)) %>%
        mutate(petitioner_counsel = gsub("\\bP\\.O\\..*", "", petitioner_counsel),
               respondent_counsel = gsub("\\bP\\.O\\..*", "", respondent_counsel)) %>%
        mutate(petitioner_counsel = gsub("\\b PO .*", "", petitioner_counsel),
               respondent_counsel = gsub("\\b PO .*", "", respondent_counsel)) %>%
        mutate(petitioner_counsel = gsub("\\#.*", "", petitioner_counsel),
               respondent_counsel = gsub("\\#.*", "", respondent_counsel)) %>%
        mutate(petitioner_counsel = gsub("^((?:[^ ]* ){2}[^ ]*(?: Jr\\.| Sr\\.| II| III)\\b).*", "\\1", petitioner_counsel),
               respondent_counsel = gsub("^((?:[^ ]* ){2}[^ ]*(?: Jr\\.| Sr\\.| II| III)\\b).*", "\\1", respondent_counsel)) %>%
        mutate(petitioner_counsel = gsub("^((?:[^ ]* ){2}[^ ]*(?: Jr\\.| Sr\\.|II|III)?).*", "\\1", petitioner_counsel),
               respondent_counsel = gsub("^((?:[^ ]* ){2}[^ ]*(?: Jr\\.| Sr\\.|II|III)?).*", "\\1", respondent_counsel)) %>%
        mutate(petitioner_counsel = gsub("[0-9]+\\s*$", "", petitioner_counsel),
               respondent_counsel = gsub("[0-9]+\\s*$", "", respondent_counsel)) %>%
        mutate(petitioner_counsel = gsub("\\d", "", petitioner_counsel),
               respondent_counsel = gsub("\\d", "", respondent_counsel))

      if (is.na(docket_entries$petitioner)) {
        docket_entries$petitioner_counsel <- NA
      } else {
        if (grepl(docket_entries$petitioner, docket_entries$petitioner_counsel, ignore.case = TRUE)) {
          docket_entries$petitioner_counsel <- docket_entries$petitioner
        }
      }

      if (is.na(docket_entries$respondent)) {
        docket_entries$respondent_counsel <- NA
      } else {
        if (grepl(docket_entries$respondent, docket_entries$respondent_counsel, ignore.case = TRUE)) {
          docket_entries$respondent_counsel <- docket_entries$respondent
        }
      }


    } #Extracting Counsel Info
  } #Counsel
  {
    months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months) {
        original_text <- gsub(paste0("(\n)", month), paste0("\n###\n", month), original_text)
      }

      docket_entries$most_recent_order_check[i] <- original_text
    }

    split_rows <- strsplit(docket_entries$most_recent_order_check, "\n###\n")


    filtered_rows <- lapply(split_rows, function(row) {
      most_recent_orders <- grepl(paste(months, collapse = "|"), row, ignore.case = TRUE)
      row[most_recent_orders]
    })


    filtered_rows <- lapply(filtered_rows, function(row) {
      row <- gsub("\n\n.*", "", row)
      row <- row[!grepl("Party name", row)]
      row <- row[!grepl("SEARCH TIPS", row, ignore.case = T)]
      row
    })

    filtered_rows <- lapply(filtered_rows, function(x) tail(x, 1))

    cleaned_rows <- lapply(filtered_rows, function(row) {
      modified_row <- gsub("\n\n", " \n\n ", row)
      modified_row <- gsub("\\n", " ", modified_row)
      modified_row <- gsub(" Main.*", "", modified_row)
      split_text <- strsplit(modified_row, " \n\n ")[[1]]
      split_text[1]
    })

    nested_list <- lapply(cleaned_rows, function(row) list(row))

    replace_empty <- function(lst) {
      modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", "", x))
      return(modified_lst)
    }

    nested_list <- replace_empty(nested_list)

    docket_entries$most_recent_order <- sapply(nested_list, function(x) paste(unlist(x), collapse = "; "))

  } #Most Recent Order
  {
    months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

    for (i in 1:nrow(docket_entries)) {
      original_text <- docket_entries$text_original[i]

      for (month in months) {
        original_text <- gsub(paste0("(\n)", month), paste0("\n###\n", month), original_text)
      }

      docket_entries$most_recent_order_check[i] <- original_text
    }

    split_rows <- strsplit(docket_entries$most_recent_order_check, "\n###\n")

    # Remove lines containing "\nParty name"
    split_rows <- lapply(split_rows, function(row) {
      row <- gsub("\n\n.*", "", row)
      row <- gsub("\n.*", "", row)
      row <- row[!grepl("Party name", row)]
      row <- row[!grepl("SEARCH TIPS", row, ignore.case = T)]
      row
    })


    filtered_rows <- lapply(split_rows, function(row) {
      row <- gsub("\n\n.*", "", row, perl = TRUE)
      row <- gsub("\nMain.*", "", row)
      row <- gsub("\nAttorneys for (Petitioner|Plaintiff|Petitioners|Plaintiff|Appellant|Appellants|Applicant|Applicants).*", "", row)
      row <- gsub("\n", "", row, perl = TRUE)
      row
    })

    nested_list <- lapply(filtered_rows, function(row) list(row))

    replace_empty <- function(lst) {
      modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", "", x))
      return(modified_lst)
    }

    nested_list <- replace_empty(nested_list)

    docket_entries$all_docket_entries <- sapply(nested_list, function(x) paste(unlist(x), collapse = "; "))
  } #All Dated Entries & Orders
  {

    docket_entries <- docket_entries %>%
      mutate(docket_number = gsub("No. ", "", docket_number)) %>%
      mutate(petition_type = type) %>%
      mutate(amicus_indicator = ifelse(amicus_indicator == 1, "Yes", "No")) %>%
      select(docket_number, petition_type, petitioner, petitioner_counsel, all_petitioner_counsel, respondent, respondent_counsel, all_respondent_counsel, all_other_counsel, docketed, submitted_to, referred_to_court, application_type, linked_with, lower_court, lower_court_case_number, lower_court_decision_date, amicus_indicator, amicus_filers, amicus_count, first_conference_date, conference_count, multiple_conference_dates, most_recent_order, all_docket_entries, majority_opinion_writer, opinion_type, number_of_opinions, opinions_by_type, opinion_filings, argument_date, special_filing, docket_url)
    docket_entries[docket_entries == ""] <- NA




  } #Final Cleaning (Arrange columns & convert bytes to UTF-8)

  return(docket_entries)

}

docket_call <- function(urls, rate, sleep) {
  docket_frame <- data.frame(url = character(), text = character(), stringsAsFactors = FALSE)
  error_count <- 0
  url_counter <- 0

  for (i in seq(1, length(urls), by = rate)) {
    batch_urls <- urls[i:min(i+rate-1, length(urls))]
    for (j in seq_along(batch_urls)) {
      url <- batch_urls[j]
      try_count <- 0
      while (try_count < 6) {
        tryCatch({
          text <- gettxt(url, encoding = "UTF-8")
          docket_frame <- rbind(docket_frame, data.frame(url = url, text = text, stringsAsFactors = FALSE))
          error_count <- 0  # Reset error count if there was a successful retrieval
          url_counter <- url_counter + 1  # Increment the URL counter
          if (url_counter %% 500 == 0) {
            cat(paste("Completed Docket:", url_counter, "\n"))
          }
        }, error = function(e) {
          error_count <- error_count + 1
          if (error_count == 1) {
            cat(paste("Error occurred with URL:", url, "\n"))
            cat(paste("Waiting 1 minute, then trying again...\n"))
            Sys.sleep(60)  # Pause for 1 minute
            try_count <- try_count + 1
          } else if (error_count == 21) {
            cat(paste("Could Not Collect From URL:", url, "\n"))
            cat(paste("Stopping Function. Please Ensure Docket Number Written Correctly and Try Again\n"))
            break  # Exit the inner loop
          } else {
            cat(paste("Error occurred with URL:", url, "\n"))
            cat(paste("Waiting 1 minute, then trying again...\n"))
            Sys.sleep(60)  # Pause for 1 minute
            try_count <- try_count + 1
          }
        })
        if (error_count == 0) {
          break
        }
      }
    }
    if (error_count == 21) {
      break
    }
    if (i+4999 < length(urls)) {
      cat("Pausing for 30 seconds...\n")
      Sys.sleep(30)
    }
  }

  return(docket_frame)
} # Call to Docket via Internet

include_func <- function(docket_entities, cols){
  if (!is.null(cols)) {
    docket_entities <- docket_entities %>%
      select(all_of(cols))
  }
  return(docket_entities)
} #Include Parameter

exclude_func <- function(docket_entities, cols){
  if (!is.null(cols)) {
    docket_entities <- docket_entities %>%
      select(-cols)
  }
  return(docket_entities)
} #Exclude Parameter

write_csv_func <- function(docket_entries, write_csv) {
  if (write_csv) {
    cat("Code to Save Dataframe as (.csv):\n")
    cat("library(utils)\n")
    cat("write.csv(<SEARCH QUERY OBJECT NAME>, file = '<SAVE FILE>.csv', row.names = FALSE)\n")
  }
}

write_xlsx_func <- function(docket_entries, write_xlsx) {
  if (write_xlsx) {
    cat("Code to Save Dataframe as (.xlsx):\n")
    cat("library(writexl)\n")
    cat("write_xlsx(<SEARCH QUERY OBJECT NAME>, path = '<SAVE FILE>.xlsx')\n")
  }
}

write_reactable_func <- function(docket_entries, write_reactable){
  if (write_reactable){
    cat("Code to Create (.HTML) Table Using Reactable:\n")
    cat("library(reactable); library(reactablefmtr)\n")
    cat("reactable(docket_entries, searchable = T,\n defaultPageSize = 20,\n theme = fivethirtyeight(font_size = 12, font_color = 'grey',\n cell_padding = 6)) %>%\n")
    cat("add_title('<YOUR TITLE HERE>') %>%\n")
    cat("add_subtitle('<YOUR SUBTITLE HERE>')\n")
    }
}

docket_search_flat <- function(docket_id, rate = 5000, sleep = 30, include = NULL, exclude = NULL, write_csv = FALSE, write_xlsx = FALSE, write_reactable = FALSE) {
  urls <- suppressWarnings(process_docket_id(docket_id))
  urls <- gsub(" ", "", urls)
  urls <- gsub("- ", "-", urls)
  urls <- gsub(" -", "-", urls)

  docket_entries <- NULL
  completed_count <- 0
  final_urls <- c()
  retry_urls <- c()
  failed_urls <- c()
  non_collect <- c()

  process_url <- function(url, docket_entries) {
    docket_frame <- suppressWarnings(docket_call(url, sleep))
    docket_frame$text <- gsub("\\xe2\\x80\\xa2", " ", docket_frame$text)
    docket_frame$text <- trimws(docket_frame$text)
    docket_entities <- suppressWarnings(clean_docket_frame(docket_frame = docket_frame))

    if (!is.null(include)) {
      docket_entities <- include_func(docket_entities, include)
    }

    if (!is.null(exclude)) {
      docket_entities <- exclude_func(docket_entities, exclude)
    }

    if (is.null(docket_entries))
      docket_entries <- docket_entities
    else
      docket_entries <- rbind(docket_entries, docket_entities)

    write_csv_func(docket_entities, write_csv)
    write_xlsx_func(docket_entities, write_xlsx)
    write_reactable_func(docket_entries, write_reactable)

    completed_count <<- completed_count + 1

    if (completed_count %% 50 == 0) {
      message("Successfully Retrieved ", completed_count, " Docket Sheets")
    }

    return(docket_entries)
  }

  for (url in urls) {
    tryCatch({
      docket_entries <- process_url(url, docket_entries)
    }, error = function(e) {
      docket_number <- gsub(".*docketfiles\\/", "", url)
      docket_number <- gsub(".*(/Public/)", "", docket_number, ignore.case = TRUE)
      docket_number <- gsub("\\.html", "", docket_number)
      docket_number <- gsub("\\.htm", "", docket_number)
      message(paste("Error Retrieving and Cleaning Docket Information from Docket ID:", docket_number))
      retry_urls <<- c(retry_urls, url)
      message("Saving URL Information and Trying Again Later")
      message("Waiting 10 Seconds Before Moving On...")
      Sys.sleep(10)
      cat("Resuming Collection Effort\n")
    })
  }

  if (length(retry_urls) > 0) {
    docket_url_newer <- "https://www.supremecourt.gov/search.aspx?filename=/docket/docketfiles/html/public/"
    docket_url_older <- "https://www.supremecourt.gov/search.aspx?filename=/docketfiles/"
    for (retry_url in retry_urls) {
      message("\nBeginning Second Attempt at Processing...\n")
      if (grepl("\\.html", retry_url)) {
        docket_number <- gsub(".*(/Public/)", "", retry_url, ignore.case = TRUE)
        docket_number <- gsub("\\.html", "", docket_number)
        docket_year <- gsub("\\-.*", "", docket_number)
        docket_year <- as.numeric(docket_year)
        if (as.numeric(docket_year) == 16) {
          retry_url <- paste0(docket_url_older, docket_number, ".htm")
        } else {
          retry_url <- paste0(docket_url_newer, docket_number, ".html")
        }
      } else {
        docket_number <- gsub(".*docketfiles\\/", "", retry_url)
        docket_number <- gsub("\\.htm", "", docket_number)
        docket_year <- gsub("\\-.*", "", docket_number)
        docket_year <- as.numeric(docket_year)
        if (as.numeric(docket_year) == 16) {
          retry_url <- paste0(docket_url_newer, docket_number, ".html")
        } else {
          retry_url <- paste0(docket_url_older, docket_number, ".htm")
        }
      }

      tryCatch({
        docket_entries <- process_url(retry_url, docket_entries)
      }, error = function(e) {
        message(paste("Error In Second Attempt -- Adjusting HTTP Conditions & Trying Again Later ( Docket ID:", docket_number, ")"))
        final_urls <<- c(final_urls, retry_url)
      })
    }
  }

  if (length(final_urls) > 0) {
    docket_url_newer <- "https://www.supremecourt.gov/search.aspx?filename=/docket/docketfiles/html/public/"
    docket_url_older <- "https://www.supremecourt.gov/search.aspx?filename=/docketfiles/"
    for (final_url in final_urls) {
      if (grepl("\\.html", final_url)) {
        docket_number <- gsub(".*(/Public/)", "", final_url, ignore.case = TRUE)
        docket_number <- gsub("\\.html", "", docket_number)
        final_url <- paste0(docket_url_older, docket_number, ".htm")
      } else {
        docket_number <- gsub(".*docketfiles\\/", "", final_url)
        docket_number <- gsub("\\.htm", "", docket_number)
        final_url <- paste0(docket_url_newer, docket_number, ".html")
      }

      tryCatch({
        docket_entries <- process_url(final_url, docket_entries)
      }, error = function(e) {
        message(paste("Error In Final Attempt -- Saving For Completion Report ( Docket ID:", docket_number, ")"))
        non_collect <<- c(non_collect, final_url)
      })
    }
  }


  if (length(non_collect) > 0) {
    non_collect <- gsub(".*(/Public/)", "", non_collect, ignore.case = TRUE)
    non_collect <- gsub(".*docketfiles\\/", "", non_collect)
    non_collect <- gsub(".html", "", non_collect)
    non_collect <- gsub(".htm", "", non_collect)
    #cat("\nFailed to Retrieve Docket Information for: ")
    #cat(non_collect, sep = ifelse(length(non_collect) > 1, ", ", ""))
  }

  return(docket_entries)
}

docket_search <- function(docket_id, rate = 5000, sleep = 30, include = NULL, exclude = NULL, write_csv = FALSE, write_xlsx = FALSE, write_reactable = FALSE) {
  urls <- suppressWarnings(process_docket_id(docket_id))
  urls <- gsub(" ", "", urls)
  urls <- gsub("- ", "-", urls)
  urls <- gsub(" -", "-", urls)
  cat("\nDocket Sheets to Collect: ", length(unique(urls)), "\n")

  docket_entries <- NULL
  completed_count <- 0
  final_urls <- c()
  retry_urls <- c()
  failed_urls <- c()
  non_collect <- c()

  process_url <- function(url, docket_entries) {
    docket_frame <- suppressWarnings(docket_call(url, sleep))
    docket_frame$text <- gsub("\\xe2\\x80\\xa2", " ", docket_frame$text)
    docket_frame$text <- trimws(docket_frame$text)
    docket_entities <- suppressWarnings(clean_docket_frame(docket_frame = docket_frame))

    if (!is.null(include)) {
      docket_entities <- include_func(docket_entities, include)
    }

    if (!is.null(exclude)) {
      docket_entities <- exclude_func(docket_entities, exclude)
    }

    if (is.null(docket_entries))
      docket_entries <- docket_entities
    else
      docket_entries <- rbind(docket_entries, docket_entities)

    write_csv_func(docket_entities, write_csv)
    write_xlsx_func(docket_entities, write_xlsx)
    write_reactable_func(docket_entries, write_reactable)

    completed_count <<- completed_count + 1

    if (completed_count %% 50 == 0) {
      message("Successfully Retrieved ", completed_count, " Docket Sheets")
    }

    return(docket_entries)
  }

  for (url in urls) {
    tryCatch({
      docket_entries <- process_url(url, docket_entries)
    }, error = function(e) {
      docket_number <- gsub(".*docketfiles\\/", "", url)
      docket_number <- gsub(".*(/Public/)", "", docket_number, ignore.case = TRUE)
      docket_number <- gsub("\\.html", "", docket_number)
      docket_number <- gsub("\\.htm", "", docket_number)
      message(paste("Error Retrieving and Cleaning Docket Information from Docket ID:", docket_number))
      retry_urls <<- c(retry_urls, url)
      message("Saving URL Information and Trying Again Later")
      message("Waiting 10 Seconds Before Moving On...")
      Sys.sleep(10)
      cat("Resuming Collection Effort\n")
    })
  }

  if (length(retry_urls) > 0) {
    docket_url_newer <- "https://www.supremecourt.gov/search.aspx?filename=/docket/docketfiles/html/public/"
    docket_url_older <- "https://www.supremecourt.gov/search.aspx?filename=/docketfiles/"
    for (retry_url in retry_urls) {
      message("\nBeginning Second Attempt at Processing...\n")
      if (grepl("\\.html", retry_url)) {
        docket_number <- gsub(".*(/Public/)", "", retry_url, ignore.case = TRUE)
        docket_number <- gsub("\\.html", "", docket_number)
        docket_year <- gsub("\\-.*", "", docket_number)
        docket_year <- as.numeric(docket_year)
        if (as.numeric(docket_year) == 16) {
          retry_url <- paste0(docket_url_older, docket_number, ".htm")
        } else {
          retry_url <- paste0(docket_url_newer, docket_number, ".html")
        }
      } else {
        docket_number <- gsub(".*docketfiles\\/", "", retry_url)
        docket_number <- gsub("\\.htm", "", docket_number)
        docket_year <- gsub("\\-.*", "", docket_number)
        docket_year <- as.numeric(docket_year)
        if (as.numeric(docket_year) == 16) {
          retry_url <- paste0(docket_url_newer, docket_number, ".html")
        } else {
          retry_url <- paste0(docket_url_older, docket_number, ".htm")
        }
      }

      tryCatch({
        docket_entries <- process_url(retry_url, docket_entries)
      }, error = function(e) {
        message(paste("Error In Second Attempt -- Adjusting HTTP Conditions & Trying Again Later ( Docket ID:", docket_number, ")"))
        final_urls <<- c(final_urls, retry_url)
      })
    }
  }

  if (length(final_urls) > 0) {
    docket_url_newer <- "https://www.supremecourt.gov/search.aspx?filename=/docket/docketfiles/html/public/"
    docket_url_older <- "https://www.supremecourt.gov/search.aspx?filename=/docketfiles/"
    for (final_url in final_urls) {
      if (grepl("\\.html", final_url)) {
        docket_number <- gsub(".*(/Public/)", "", final_url, ignore.case = TRUE)
        docket_number <- gsub("\\.html", "", docket_number)
        final_url <- paste0(docket_url_older, docket_number, ".htm")
      } else {
        docket_number <- gsub(".*docketfiles\\/", "", final_url)
        docket_number <- gsub("\\.htm", "", docket_number)
        final_url <- paste0(docket_url_newer, docket_number, ".html")
      }

      tryCatch({
        docket_entries <- process_url(final_url, docket_entries)
      }, error = function(e) {
        message(paste("Error In Final Attempt -- Saving For Completion Report ( Docket ID:", docket_number, ")"))
        non_collect <<- c(non_collect, final_url)
      })
    }
  }


  cat("\n- - - - - - - - COMPLETION SUMMARY - - - - - - - -")
  cat("\nTotal Docket Sheets Successfully Retrieved:", length(docket_entries$docket_number))
  cat("\nTotal Docket Sheets Failed to Retrieve:", length(failed_urls))
  cat("\nDocket Types Retrieved...")
  cat("\n   Docketed Petitions: ", length(docket_entries$petition_type[docket_entries$petition_type == "Docketed Case"]))
  cat("\n   Docketed Petitions (Original Jurisdiction): ", length(docket_entries$petition_type[docket_entries$petition_type == "Docketed Case - Original Jurisdiction"]))
  cat("\n   Applications: ", length(docket_entries$petition_type[docket_entries$petition_type == "Application"]))
  cat("\n   Motions: ", length(docket_entries$petition_type[docket_entries$petition_type == "Motion"]))

  if (length(non_collect) > 0) {
    non_collect <- gsub(".*(/Public/)", "", non_collect, ignore.case = TRUE)
    non_collect <- gsub(".*docketfiles\\/", "", non_collect)
    non_collect <- gsub(".html", "", non_collect)
    non_collect <- gsub(".htm", "", non_collect)
    cat("\nFailed to Retrieve Docket Information for: ")
    cat(non_collect, sep = ifelse(length(non_collect) > 1, ", ", ""))
  }

  return(docket_entries)
}

print_flattened_list <- function(column) {
  flattened_list <- unlist(lapply(column, function(x) strsplit(x, "; ")[[1]]))
  print(flattened_list)
}

```

## **docket_search()**

`docket_search`serves as an automated tool for collecting, parsing, and cleaning information from docketed cases, petitions, and motions to the United States Supreme Court. Implementation of `docket_search` requires providing a docket number corresponding to the petition (or application/motion) of interest as a character vector. The function call will also accept a list of docket numbers, as well as an object containing a list of comma-separated character vectors. For more information on the Supreme Court docket, *see*   [supremecourt.gov](https://www.supremecourt.gov/docket/docket.aspx).


## **Function Description**

The `docket_search` function accepts several optional parameters to customize search queries:

- `docket_id`: The docket number of interest - written as a character vector in **R**. This can take the form of filed petitions (e.g., "19-1392"), applications (e.g., "22A948"), or motions (e.g., "22M11"). `docket_id`  parameter is **REQUIRED** for all searches. 
*Note*: The function will also accept list objects containing comma-separated character vectors of docket numbers (e.g., docket_ids <- c("19-108", "19-184", "19-199", "19-251"). 

*Further*: The function will accept petitions filed pursuant to the Court's **original** jurisdiction, though it is recommended that docket numbers be written in the style similar to supremecourt.gov (e.g., "22O145").

- `rate`: The number of requests to process per function call (default is **1000**). Long, repeated calls to supremecourt.gov can produce SSL errors. Limiting the `rate` of docket queries deters incidental SSL errors, though the package is built to adapt and continue following these errors while indicating which docket filings (if any) were unsuccessfully retrieved. The function will allow up to 5 url-specific errors or 20 total errors before ending the function. Based on prior testing, an SSL error tends to yield every 4,000 to 5,000 requests.  
- `sleep`: The number of seconds to wait between docket requests (default is **30**).
- `include`: A character vector that will limit the output variables to only those requested (default is **NULL**).
- `exclude`: A character vector that will exclude any output variables requested (default is **NULL**)
- `write_csv`: Logical value indicating whether to print code to convert the output dataframe to a .csv file (default is **FALSE**).
- `write_xlsx`: Logical value indicating whether to print code to convert the output dataframe to an excel file (default is **FALSE**).
- `write_reactable`: Logical value indicating whether to print code to convert the output dataframe to a .html file using `reactable()` (default is **FALSE**).

## `docket_search` **Variables**

```{r, echo = F}
dobbs_test <- docket_search_flat(docket_id = "19-1392")
names(dobbs_test)
```


- `docket_id`: The docket number corresponding with the search query. 
- `petition_type`: Factor term indicating *Docketed Petition*, *Application*, or *Motion*.
- `petitioner`: Petitioning party of interest.
- `petitioner_counsel`: Primary Counsel of Record listed for petitioning party (or parties) of interest.
- `all_petitioner_counsel`: All listed counsel for for petitioning party (or parties) of interest.
- `petitioner_counsel_address`: Listed address of Counsel of Record for petitioning party of interest. 
- `respondent`: Responding party of interest.
- `respondent_counsel`: Primary Counsel of Record listed for responding party (or parties) of interest.
- `all_respondent_counsel`: All listed counsel for for responding party (or parties) of interest.
- `all_other_counsel`: Any other listed counsel of record.  
- `docketed`: Date the petition was docketed with the Court. 
- `submitted_to`: Denotes which Justice(s) an **Application** or **Motion** was submitted to.
- `referred_to_court``: Indicates whether the **Application** or **Motion** was referred to the full Court for consideration. 
- `application_type`: Indicates the specific relief sought by application (e.g., ***Stays***, ***Injunctions Pending Appeal***, etc.)
- `linked_with`: Indicates whether the docketed petition (or application/motion) is linked with any other docketed filings. 
- `lower_court`: The most recent lower court to take action prior to filing at SCOTUS. 
- `lower_court_case_number`: Docket number corresponding with the relevant filing of interest at the lower court. 
- `lower_court_decision_date`: Date corresponding with most recent action at lower court. 
- `amicus_indicator`: Dichotomous term indicating whether any briefs were filed as amicus curiae. 
- `amicus_filers`: A nested list containing all amicus filers (if any).
- `amcius_count`: Integer representing the total number of amicus filings (if any).
- `first_conference_date`: Date indicating the first conference where the relevant petition was considered (**Petitions Only**). 
- `conference_count`: Integer representing the number of times the petition was re-listed and considered at another conference (**Petitions Only**). 
- `multiple_conference_dates`: Dichtomous term indicating whether the petition was considered at more than one conference (**Petitions Only**). 
- `most_recent_order`: Factor indicating the most recent action taken by Court (*Docketed*, ***Petition DENIED***, ***Petition GRANTED***, ***SET FOR ARGUMENT***, ***ARGUED***, ***JUDGEMENT ISSUED***).
- `all_docket_entries`: Partitioned list of all docket entries (or orders) separated by date of entry.
- `majority_opinion_writer`: Character vector indicating justice who wrote majority opinion (**Argued and Decided Petitions Only**). 
- `opinion_type`: Factor term indicating disposition taken on petition (*DIG*, *AFFIRMED*, ***VACATED AND REMANDED***, ***REVERSED AND REMANDED***, ***No Opinion Issued***, ***GVR***).
- `number_of_filings`: Integer indicating the total number of opinions filed (***Majority Opinion*** plus any ***Concurrences*** and ***Dissents***).
- `opinions_by_type`: Nested list indicating the number of ***Concurrences*** and ***Dissents*** filed (if any). 
- `opinion_filings`: Nested list indicating which justice(s) filed each opinion. 
- `argument_date`: Date of oral argument (if any). 
- `special_filing`: Factor indicating whether filing considered writs of ***Habeas Corpus*** or ***Mandamus***, as well as whether it considered ***Capital Punishment*** (e.g., ***Stays of Execution***) or is a petition filed under the Court's ***Original Jurisdiction***.
- `docket_url`: Http address corresponding with location of docket of interest on supremecourt.gov.

## **Example Walkthrough**

Here's an example of how to use the `docket_search` function using *Dobbs v. Jackson Women's Health Clinic* (2022), one of the largest docket sheets hosted by the Supreme Court:


```{r, eval = F}
#Load scotustext package
install.packages("scotustext")
library(scotustext)
```

```{r}
#Call to Docket Using Docket Number for Dobbs v. Jackson (19-1392)
dobbs_test <- docket_search(docket_id = "19-1392")
```

**Note**: Variables where multiple elements are returned (*e.g., multiple amici curiae filers*) are stored as flattended lists to allow for exporting to (.csv) and (.xlsx). However, these can be converted back to their original structure using the function below: 

```{r, eval = F}
print_flattened_list <- function(column) {
  if (length(column) > 1) {
    for (row in column) {
      if (length(row) > 0) {
        elements <- unlist(strsplit(row, "; "))
        print(list(elements))
      } else {
        print(list())
      }
    }
  } else {
    nested_list <- lapply(column[[1]], function(element) list(unlist(strsplit(element, "; "))))
    print(nested_list)
  }
}
print_flattened_list(<DOCKET OBJECT AND INDEX COLUMN>)
```

```{r}
#List of Conferences Where Dobbs Was Considered
print_flattened_list(dobbs_test$multiple_conference_dates)

#List of Opinions Filed
print_flattened_list(dobbs_test$opinion_filings)

#List of Amicus Filers
print_flattened_list(dobbs_test$amicus_filers)

#List Counsel (Petitioner)
print_flattened_list(dobbs_test$all_petitioner_counsel)

#List Counsel (Respondent)
print_flattened_list(dobbs_test$all_respondent_counsel)

#List Counsel (Other)
print_flattened_list(dobbs_test$all_other_counsel)
```
