---
title: "scotustext (CRAN)"
author:
- name: Jake S. Truscott, Ph.D
  affiliation: University of Georgia
date: "`r Sys.Date()`"
output: html_document
---


<style type="text/css">
  body{
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(scotustext)
library(tidyverse)
library(tidytext)
library(tm)
library(plyr)
library(textdata)
library(dplyr)
library(purrr)
library(tidyr)
library(ggplot2)
library(data.table)
library(ggrepel)
library(lubridate)
library(strex)
library(utils)
library(anytime)
library(zoo)
library(rvest)
library(webshot)
library(htmltools)
library(pdftools)
library(stringr)
library(htm2txt)
library(sjPlot)
library(reactable)
library(reactablefmtr)
library(httr)
library(devtools)

 process_docket_id <- function(docket_id) {
    docket_url_newer <- "https://www.supremecourt.gov/search.aspx?filename=/docket/docketfiles/html/public/"
    docket_url_older <- "https://www.supremecourt.gov/search.aspx?filename=/docketfiles/"
    term <- as.data.frame(docket_id)
    term <- term %>%
      mutate(type = 3) %>%
      mutate(type = ifelse(grepl("m", docket_id, ignore.case = T), 2, type)) %>%
      mutate(type = ifelse(grepl("a", docket_id, ignore.case = T), 1, type)) %>%
      mutate(type = ifelse(grepl("o", docket_id, ignore.case = T), 4, type)) %>%
      mutate(year = as.numeric(gsub("\\-.*|a.*|A.*|m.*|M.*|Original.*|original.*|o.*|O.*|Orig.*|orig.*", "", docket_id))) %>%
      mutate(docket_number = gsub(".*\\-|.*a|.*A|.*m|.*M|.*Original|.*original|.*o|.*O|.*Orig|.*orig", "", docket_id)) %>%
      mutate(url = ifelse(as.numeric(year) < 10, 
                          ifelse(type == 1, paste0(docket_url_older, "0", year, "a", docket_number, ".htm"),
                                 ifelse(type == 2, paste0(docket_url_older, "0", year, "m", docket_number, ".htm"),
                                        ifelse(type == 3, paste0(docket_url_older, "0", year, "-", docket_number, ".htm"),
                                               ifelse(type == 4, paste0(docket_url_older, "0", year, "o", docket_number, ".htm"), NA)
                                        )
                                 )
                          ),
                          ifelse(as.numeric(year) >= 10,
                                 ifelse(as.numeric(year) >= 17,
                                        ifelse(type == 1, paste0(docket_url_newer, year, "a", docket_number, ".html"),
                                               ifelse(type == 2, paste0(docket_url_newer, year, "m", docket_number, ".html"),
                                                      ifelse(type == 3, paste0(docket_url_newer, year, "-", docket_number, ".html"),
                                                             ifelse(type == 4, paste0(docket_url_newer, year, "o", docket_number, ".html"), NA)
                                                      )
                                               )
                                        ),
                                        ifelse(as.numeric(year) < 17,
                                               ifelse(type == 1, paste0(docket_url_newer, year, "a", docket_number, ".htm"),
                                                      ifelse(type == 2, paste0(docket_url_newer, year, "m", docket_number, ".htm"),
                                                             ifelse(type == 3, paste0(docket_url_newer, year, "-", docket_number, ".htm"),
                                                                    ifelse(type == 4, paste0(docket_url_newer, year, "o", docket_number, ".htm"), NA)
                                                             )
                                                      )
                                               ),
                                               NA
                                        )
                                 ),
                                 NA
                          )
      ))
    urls <- term$url
    return(urls)
  }

clean_docket_frame <- function(docket_frame, include, exclude){

  {
    {
      corpus <- tm::Corpus(VectorSource(docket_frame[["text"]]))
      corpus <- tm_map(corpus, content_transformer(gsub), pattern = "\\xe2\\x80\\xa2", replacement = " ")
      corpus <- tm_map(corpus, stripWhitespace)
      docket_entries <- data.frame(text = sapply(corpus, as.character), stringsAsFactors = FALSE) #Convert Corpus to Dataframe
      removeWordsWithBackslash <- function(inputString) {
        outputString <- gsub("\\S*\\\\\\\\\\S*\\s?", "", inputString)
        outputString <- iconv(outputString, "UTF-8", "ASCII", sub="")
        return(outputString)}
      docket_entries$text <- sapply(docket_entries$text, removeWordsWithBackslash)
    } #Base Clean (Corpus -> Toss "\\")
    {
      docket_entries$docket_id <- docket_frame$url
      docket_entries$docket_url <- docket_frame$url
      docket_entries$docket_id <- gsub(".*(/Public/)", "", docket_entries$docket_id, ignore.case = TRUE)
      docket_entries$docket_id <- gsub(".*docketfiles\\/", "", docket_entries$docket_id )
      docket_entries$docket_id <- gsub(".html", "", docket_entries$docket_id)
      docket_entries$docket_id <- gsub(".htm", "", docket_entries$docket_id)
      docket_entries$docket_number <- docket_entries$docket_id
      docket_entries$text_original <- docket_entries$text
      docket_entries <- separate(docket_entries, col = text, into = c("toss", "text"), sep = "Title: ", extra = "merge")
      docket_entries <- docket_entries %>% select(-c(toss))
      docket_entries <- docket_entries %>%
        mutate(text_original = text) %>%
        select(text_original, docket_id, docket_url, docket_number, text)
      docket_entries$text <- gsub("In Re Grand Jury", "In Re Grand Jury, Petitioner ", docket_entries$text)
      docket_entries <- separate(docket_entries, col = text, into = c("petitioner", "text"), sep = ", (Petitioner|Plaintiff|Petioners|Plaintiffs|Appellant|Appellants|In Re|Applicant|Applicants)", extra = "merge")
      docket_entries <- separate(docket_entries, col = text, into = c("respondent", "text"), sep = "Docketed: ", extra = "merge")
      docket_entries$respondent <- gsub("\n", " ", docket_entries$respondent)
      docket_entries$respondent <- gsub(".*v. ", "", docket_entries$respondent)
      docket_entries$respondent <- paste0(" ", docket_entries$respondent)
      docket_entries$respondent <- gsub(" s ", "", docket_entries$respondent)
      docket_entries$respondent <- trimws(docket_entries$respondent)
      docket_entries$petitioner <- gsub("\\*\\*\\* CAPITAL CASE \\*\\*\\*", "", docket_entries$petitioner)
      docket_entries$petitioner <- trimws(docket_entries$petitioner)

      docket_entries <- separate(docket_entries, col = text, into = c("docketed", "text"), sep = "(Lower Ct: |~Date)", extra = "merge")
      docket_entries <- separate(docket_entries, col = text, into = c("lower_court", "text"), sep = "(Case Numbers: |Case Nos.: )", extra = "merge")
      docket_entries <- separate(docket_entries, col = text, into = c("lower_court_case_number", "text"), sep = "Decision Date: ", extra = "merge")
      docket_entries <- separate(docket_entries, col = text, into = c("lower_court_decision_date", "text"), sep = " ", extra = "merge")
      docket_entries <- separate(docket_entries, col = text, into = c("lower_court_decision_date2", "text"), sep = " ", extra = "merge")
      docket_entries <- separate(docket_entries, col = text, into = c("lower_court_decision_date3", "text"), sep = " ", extra = "merge")
      docket_entries$lower_court_decision_date <- paste0(docket_entries$lower_court_decision_date, " ", docket_entries$lower_court_decision_date2, " ", docket_entries$lower_court_decision_date3)
      docket_entries <- docket_entries %>% select(-c(lower_court_decision_date2, lower_court_decision_date3, docket_id))
      docket_entries <- separate(docket_entries, col = text, into = c("lower_court_rehearing_denied", "text"), sep = "Proceedings and Orders ", extra = "merge")
      docket_entries$lower_court_rehearing_denied <- gsub("Rehearing Denied: ", "", docket_entries$lower_court_rehearing_denied)
      docket_entries$lower_court_rehearing_denied <- gsub("Date", "", docket_entries$lower_court_rehearing_denied)
      docket_entries$lower_court_rehearing_denied<- gsub("^([^ ]+ [^ ]+ [^ ]+).*", "\\1", docket_entries$lower_court_rehearing_denied)
      docket_entries$lower_court_rehearing_denied <- ifelse(docket_entries$lower_court_rehearing_denied == "Discretionary Court Decision", "", docket_entries$lower_court_rehearing_denied)
      docket_entries$lower_court_rehearing_denied <- ifelse(docket_entries$lower_court_rehearing_denied == "Court Decision :", "", docket_entries$lower_court_rehearing_denied)
      docket_entries$lower_court_decision_date <- ifelse(docket_entries$lower_court_decision_date == "Rehearing Denied: Discretionary", "", docket_entries$lower_court_decision_date)
      docket_entries$lower_court_decision_date <- ifelse(docket_entries$lower_court_decision_date == "Rehearing Denied:", "", docket_entries$lower_court_decision_date)
      docket_entries$file_type <- ifelse(grepl("in forma pauperis", docket_entries$text), "IFP", "Paid")
      #docket_entries$amicus_indicator <- ifelse(grepl("brief amic", docket_entries$text), "Amici Filed", "No Amici")
      docket_entries$text2<- iconv(docket_entries$text_original, to = "UTF-8")
      #docket_entries$amicus_count <- str_count(docket_entries$text_original, "brief amic[i|us]")
      docket_entries <- separate(docket_entries, col = text2, into = c("pre_conference", "post_conference"), sep = "DISTRIBUTED for Conference of ", extra = "drop", fill = "right", convert = FALSE)
      # docket_entries$amicus_pre_merits_count <- str_count(docket_entries$pre_conference, "brief amic[i|us]")
      docket_entries <- separate(docket_entries, col = post_conference, into = c("conference_date", "toss"), sep = "\\.(?=\\s)", extra = "drop", fill = "right", convert = FALSE )
      docket_entries <- docket_entries %>% select(-c(toss, pre_conference))

      docket_entries$conference_text <- iconv(docket_entries$text_original, to = "UTF-8")
      docket_entries$conference_count <- str_count(docket_entries$conference_text, "DISTRIBUTED for Conference")

      docket_entries <- docket_entries %>%
        select(-c(conference_text))

      docket_entries$certiorari <- ifelse(grepl("Petition DENIED", docket_entries$text_original), "Denied", "Granted")

      docket_entries <- docket_entries %>%
        mutate(special_filing = ifelse(
          grepl("mandamus", text_original, ignore.case = T), "Mandamus", ifelse(grepl("habeas", text_original, ignore.case = T), "Habeas", ifelse(grepl("capital case", text_original, ignore.case = T), "Capital Case", ifelse(grepl("o", docket_number, ignore.case = T), "Original Jurisdiction", NA)))))

      docket_entries$rehearing_filed <- ifelse(grepl("Rehearing filed", docket_entries$text_original), "Rehearing Filed", "No Rehearing Petition")
      docket_entries$rehearing_order <- ifelse(docket_entries$rehearing_filed == "No Rehearing Petition", " ", ifelse(grepl("Rehearing DENIED", docket_entries$text_original), "Rehearing Denied", "Rehearing Granted"))
      docket_entries$text <- docket_entries$text_original
      docket_entries <- separate(docket_entries, col = text, into = c("text", "pc"), sep = "Attorneys for (Petitioner|Plaintiff|Petioners|Plaintiff)", extra = "merge")
      docket_entries <- separate(docket_entries, col = pc, into = c("petitioner_counsel", "text"), sep = "Party ", extra = "merge")
      docket_entries$petitioner_counsel <- paste0(" ", docket_entries$petitioner_counsel)
      docket_entries$petitioner_counsel <- gsub(" s ", "", docket_entries$petitioner_counsel)
      docket_entries$petitioner_counsel <- trimws(docket_entries$petitioner_counsel)
      docket_entries$petitioner_counsel <- gsub("Counsel of Record ", "", docket_entries$petitioner_counsel)
      docket_entries$petitioner_counsel <- trimws(docket_entries$petitioner_counsel)

      docket_entries$respondent_counsel <- ifelse(grepl("for Respondent", docket_entries$text), gsub(".*(for Respondent)", "", docket_entries$text, ignore.case = TRUE), "" )
      docket_entries <- separate(docket_entries, col = respondent_counsel, into = c("respondent_counsel", "text"), sep = " Party ", extra = "merge")
      docket_entries$respondent_counsel <- paste0(" ", docket_entries$respondent_counsel)
      docket_entries$respondent_counsel <- gsub(" s ", "", docket_entries$respondent_counsel)
      docket_entries$respondent_counsel <- trimws(docket_entries$respondent_counsel)
      docket_entries$respondent_counsel <- gsub("Counsel of Record ", "", docket_entries$respondent_counsel)
      docket_entries$respondent_counsel <- trimws(docket_entries$respondent_counsel)

      docket_entries <- docket_entries %>%
        mutate(type = case_when(
          grepl("a", docket_number, ignore.case = T) ~ "Application",
          grepl("m", docket_number, ignore.case = T) ~ "Motion",
          grepl("-", docket_number, ignore.case = T) ~ "Docketed Case",
          grepl("o", docket_number, ignore.case = T) ~ "Docketed Case"
        )) %>%
        filter(!is.na(text_original))

      docket_entries$lower_court_rehearing_denied[grep("~", docket_entries$lower_court_rehearing_denied)] <- ""
      docket_entries$lower_court_rehearing_denied[grep("=", docket_entries$lower_court_rehearing_denied)] <- ""
      docket_entries$lower_court_rehearing_denied[grep("<", docket_entries$lower_court_rehearing_denied)] <- ""
      docket_entries$lower_court_rehearing_denied[grep(">", docket_entries$lower_court_rehearing_denied)] <- ""

      docket_entries <- docket_entries %>%
        mutate(linked_with = ifelse(grepl("linked with", docketed, ignore.case = T), gsub(".*Linked with ", "", docketed, ignore.case = T), "")) %>%
        mutate(docketed = ifelse(grepl("linked with", docketed, ignore.case = T), gsub(" Linked with.*", "", docketed, ignore.case = T), docketed))

      docket_entries <- docket_entries %>%
        select(-c(text))

    } #Main Cleaning and Parsing
    {
      months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]

        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }

        docket_entries$amicus_check[i] <- iconv(original_text, to = "UTF-8", sub = "")
      }

      encoded_string <- docket_entries$amicus_check
      split_rows <- strsplit(encoded_string, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_amicis_curiae_brief <- grepl("brief amici curiae|brief amicus curiae", row, ignore.case = TRUE)
        row[has_amicis_curiae_brief]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        row <- iconv(row, to = "UTF-8", sub = "")
        row <- str_remove(row, ".*amici curiae of |.*amicus curiae of ")
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        str_remove(row, " filed\\..*")
      })
      nested_list <- lapply(cleaned_rows, function(row) list(row))

      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", "", x))
        return(modified_lst)
      }

      nested_list <- replace_empty(nested_list)

      docket_entries$amicus_filers <- nested_list
      docket_entries <- docket_entries %>%
        mutate(amicus_filers = sapply(amicus_filers, function(x) paste(unlist(x), collapse = "; "))) %>%
        mutate(amicus_indicator = ifelse(is.na(amicus_filers), 0, 1)) %>%
        mutate(amicus_count = sapply(docket_entries$amicus_filers, function(x) length(unlist(x))))



    } #Amicus Filings
    {
      months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]

        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }

        docket_entries$argument_check[i] <- original_text
      }

      encoded_string <- docket_entries$argument_check
      split_rows <- strsplit(encoded_string, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_argument <- grepl("Argued\\.", row, ignore.case = TRUE)
        row[has_argument]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        row <- iconv(row, to = "UTF-8", sub = "")
        row <- str_remove(row, " Argued\\..*")
      })
      nested_list <- lapply(cleaned_rows, function(row) paste(row, collapse = ", "))

      docket_entries$argument_date <- nested_list
      docket_entries <- docket_entries %>%
        mutate(argument_date = sapply(argument_date, function(x) paste(x, collapse = "; ")))


    } #Oral Argument Date
    {
      months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")
      
      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]
        
        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }
        
        docket_entries$multiple_conference_check[i] <- original_text
      }
      
      split_rows <- strsplit(docket_entries$multiple_conference_check, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_multiple_conference <- grepl("DISTRIBUTED for Conference", row, ignore.case = TRUE)
        row[has_multiple_conference]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        str_remove(row, ".*DISTRIBUTED for Conference of ")
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        str_remove(row, "\\..*")
      })
      nested_list <- lapply(cleaned_rows, function(row) list(row))
      
      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(x == "character(0)", "", x))
        return(modified_lst)
      }
      
      nested_list <- replace_empty(nested_list)
      
      docket_entries$multiple_conference_dates <- nested_list
      docket_entries <- docket_entries %>%
        mutate(multiple_conference_dates = sapply(multiple_conference_dates, function(x) paste(unlist(x), collapse = "; ")))
      

    } #Multiple Conference Dates
    {
      months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")

      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]

        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }

        docket_entries$opinion_writer_check[i] <- original_text
      }

      split_rows <- strsplit(docket_entries$opinion_writer_check, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_opinion_writer <- grepl("delivered the opinion", row, ignore.case = TRUE)
        row[has_opinion_writer]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        str_remove(row, " delivered the opinion.*")
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(", J\\.,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(", C\\. J\\.,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        str_remove(row, ".*\\. ")
      })
      nested_list <- lapply(cleaned_rows, function(row) paste(row, collapse = ", "))

      docket_entries$majority_opinion_writer <- nested_list

      docket_entries <- docket_entries %>%
        mutate(majority_opinion_writer = sapply(majority_opinion_writer, function(x) paste(x, collapse = "; "))) %>%
        mutate(majority_opinion_writer = ifelse(grepl("opinion per curiam", text_original, ignore.case = TRUE), "Per Curiam", majority_opinion_writer))

    } #Majority Opinion Writer
    {
      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]

        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }

        docket_entries$opinion_writer_check[i] <- original_text
      }

      split_rows <- strsplit(docket_entries$opinion_writer_check, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_opinion_writer <- grepl("delivered the opinion", row, ignore.case = TRUE)
        row[has_opinion_writer]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        gsub(", J\\.,", "", row)
      })
      count_filed <- str_count(cleaned_rows, pattern = "filed")
      cleaned_rows <- str_count(cleaned_rows, pattern = "delivered") + count_filed

      docket_entries$number_of_opinions <- as.integer(cleaned_rows)
      docket_entries$number_of_opinions <- ifelse(grepl("opinion per curiam", docket_entries$text_original, ignore.case = TRUE), "Per Curiam", docket_entries$number_of_opinions)

    } #Number of Opinions Filed
    {

      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]

        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }

        docket_entries$opinion_writer_check[i] <- original_text
      }

      split_rows <- strsplit(docket_entries$opinion_writer_check, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_opinion_writer <- grepl("delivered the opinion", row, ignore.case = TRUE)
        row[has_opinion_writer]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        gsub(", J\\.,", "", row)
      })
      dissent_count <- sapply(cleaned_rows, function(row) {
        sum(grepl("dissent", row, ignore.case = TRUE))
      })
      concur_count <- sapply(cleaned_rows, function(row) {
        sum(grepl("concur", row, ignore.case = TRUE))
      })

      nested_filings <- lapply(seq_along(docket_entries$text_original), function(i) {
        list(
          dissent_count = paste0("Dissents: ", as.character(dissent_count[i])),
          concur_count = paste0("Concurrences: ", as.character(concur_count[i]))
        )
      })

      docket_entries$opinions_by_type <- nested_filings
      docket_entries <- docket_entries %>%
        mutate(opinions_by_type = sapply(opinions_by_type, function(x) paste(x, collapse = "; ")))



    } #Number of Opinions Filed (Breakdown)
    {
      months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")
      
      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]
        
        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }
        
        docket_entries$opinion_writer_check[i] <- original_text
      }
      
      split_rows <- strsplit(docket_entries$opinion_writer_check, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_opinion_writer <- grepl("delivered the opinion", row, ignore.case = TRUE)
        row[has_opinion_writer]
      })
      cleaned_rows <- lapply(filtered_rows, function(row) {
        gsub(", J\\.,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        trimws(row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(", JJ\\.\\,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(", J\\.\\,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub(", C\\. J\\.\\,", "", row)
      })
      cleaned_rows <- lapply(cleaned_rows, function(row) {
        gsub("\\. ", "\n###\n", row)
      })
      cleaned_rows <- unlist(cleaned_rows)
      split_rows <- strsplit(cleaned_rows, "\n###\n")
      
      contains_file_or_delivered <- function(row) {
        any(grepl("filed|delivered", row, ignore.case = TRUE))
      }
      
      split_rows <- lapply(split_rows, function(lst) {
        lst <- Filter(contains_file_or_delivered, lst)
        if (length(lst) > 0) {
          lst <- lst[!sapply(lst, is.null)]
        } else {
          lst <- NULL
        }
        lst
      })
      
      replace_empty <- function(lst) {
        modified_lst <- lapply(lst, function(x) ifelse(is.null(x) || length(x) == 0, list(NULL), list(x)))
        return(modified_lst)
      }
      
      split_rows <- replace_empty(split_rows)
      
      docket_entries$opinion_filings <- split_rows
      docket_entries <- docket_entries %>%
        mutate(opinion_filings = sapply(opinion_filings, function(x) ifelse(is.null(x), "", paste(unlist(x), collapse = "; "))))
      
    } #Who Filed (And Joined)
    {
      docket_entries <- docket_entries %>%
        mutate(opinion_type = case_when(
          grepl("improvidently granted", text_original, ignore.case = TRUE) ~ "DIG",
          grepl("AFFIRMED", text_original, ignore.case = TRUE) ~ "AFFIRMED",
          grepl("Judgment VACATED and case REMANDED", text_original, ignore.case = TRUE) ~ "Vacated and Remanded",
          grepl("Judgments VACATED and cases REMANDED", text_original, ignore.case = TRUE) ~ "Vacated and Remanded",
          grepl("Judgment REVERSED and case REMANDED", text_original, ignore.case = TRUE) ~ "Reversed and Remanded",
          grepl("Judgments REVERSED and cases REMANDED", text_original, ignore.case = TRUE) ~ "Reversed and Remanded",
          grepl("REVERSED", text_original, ignore.case = TRUE) ~ "Reversed"
        )) %>%
        mutate(opinion_type = ifelse(is.na(opinion_type), "No Opinion Issued", opinion_type))
      
      months <- c("Jan ", "Feb ", "Mar ", "Apr ", "May ", "Jun ", "Jul ", "Aug ", "Sep ", "Oct ", "Nov ", "Dec ")
      
      for (i in 1:nrow(docket_entries)) {
        original_text <- docket_entries$text_original[i]
        
        for (month in months) {
          original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
        }
        
        docket_entries$gvr_check[i] <- iconv(original_text, to = "UTF-8", sub = "")
      }
      
      encoded_string <- docket_entries$gvr_check
      split_rows <- strsplit(encoded_string, "\n###\n")
      filtered_rows <- lapply(split_rows, function(row) {
        has_gvr_brief <- grepl("GRANTED", row, ignore.case = TRUE) &
          grepl("VACATED", row, ignore.case = TRUE) &
          grepl("REMANDED", row, ignore.case = TRUE)
        if (any(has_gvr_brief))
          "GVR"
        else
          row
      })
      
      docket_entries$gvr <- filtered_rows
      
      docket_entries <- docket_entries %>%
        mutate(opinion_type = ifelse(gvr == "GVR", "GVR", opinion_type))
      
      
    } #Type of Decision
    {

      petitioner_counsel <- data.frame(docket_entries$petitioner_counsel)
      names(petitioner_counsel)[1] <- "petitioner_counsel"
      petitioner_counsel$petitioner_counsel <- gsub(".*\\: ", "", petitioner_counsel$petitioner_counsel)
      remove_text_after_third_space <- function(x) {
        # Split the text string into separate words
        words <- strsplit(x, " ")[[1]]

        # Remove any words beyond the third word
        truncated_words <- words[1:3]

        # Combine the truncated words back into a single string
        truncated_string <- paste(truncated_words, collapse = " ")

        # Return the truncated string
        return(truncated_string)
      } #Function to Trim Petitioner Counesl Name
      petitioner_counsel$petitioner_counsel_truncated <- sapply(petitioner_counsel$petitioner_counsel, remove_text_after_third_space) #Remove All Text After Third Space (Captures Most Names Re: First - Middle - Last)
      petitioner_counsel$petitioner_counsel_truncated <- gsub("POB", "", petitioner_counsel$petitioner_counsel_truncated )    #Remove any "PO" or "P.O"
      petitioner_counsel$petitioner_counsel_truncated <- gsub("P.O", "", petitioner_counsel$petitioner_counsel_truncated )    #Remove any "PO" or "P.O"
      petitioner_counsel$petitioner_counsel_truncated <- gsub("PO", "", petitioner_counsel$petitioner_counsel_truncated )    #Remove any "PO" or "P.O"
      petitioner_counsel$petitioner_counsel_truncated <- gsub("[[:digit:]].*", "", petitioner_counsel$petitioner_counsel_truncated )    #Remove Any Numbers
      petitioner_counsel$petitioner_counsel_truncated <- gsub("\\,", "", petitioner_counsel$petitioner_counsel_truncated )    #Remove Any Numbers
      petitioner_counsel$petitioner_counsel_truncated <- trimws(petitioner_counsel$petitioner_counsel_truncated)
      #Trim WS
      petitioner_counsel$petitioner_counsel_truncated <- gsub(" The", "", petitioner_counsel$petitioner_counsel_truncated )    #Remove any "The *Lawfirm*"
      petitioner_counsel$petitioner_counsel_truncated <- gsub("Univ.*", "", petitioner_counsel$petitioner_counsel_truncated )    #Remove any University
      petitioner_counsel$petitioner_counsel_truncated <- gsub(" \\..*", "", petitioner_counsel$petitioner_counsel_truncated )    #Remove trailing periods
      petitioner_counsel$petitioner_counsel_truncated <- ifelse(grepl("NA NA", petitioner_counsel$petitioner_counsel_truncated), "", petitioner_counsel$petitioner_counsel_truncated)

      petitioner_counsel$petitioner_counsel_address <- petitioner_counsel$petitioner_counsel


      petitioner_counsel$petitioner_counsel_address <- trimws(petitioner_counsel$petitioner_counsel_address)
      petitioner_counsel$petitioner_counsel_address <- sub("^,\\s*", "", petitioner_counsel$petitioner_counsel_address)

      petitioner_counsel <- petitioner_counsel %>%
        mutate(petitioner_counsel_truncated = ifelse(grepl("Jr.", petitioner_counsel_address), paste0(petitioner_counsel_truncated, " Jr."), petitioner_counsel_truncated)) %>%
        mutate(petitioner_counsel_truncated = ifelse(grepl("Sr.", petitioner_counsel_address), paste0(petitioner_counsel_truncated, " Sr."), petitioner_counsel_truncated)) %>%
        mutate(petitioner_counsel_truncated = ifelse(grepl("II", petitioner_counsel_address), paste0(petitioner_counsel_truncated, " II"), petitioner_counsel_truncated)) %>%
        mutate(petitioner_counsel_truncated = ifelse(grepl("III", petitioner_counsel_address) & !grepl("II", petitioner_counsel_truncated), paste0(petitioner_counsel_truncated, " III"), petitioner_counsel_truncated)) %>%
        mutate(petitioner_counsel_address = gsub("Jr.", "", petitioner_counsel_address)) %>%
        mutate(petitioner_counsel_address = gsub("Sr.", "", petitioner_counsel_address)) %>%
        mutate(petitioner_counsel_address = gsub("II.", "", petitioner_counsel_address)) %>%
        mutate(petitioner_counsel_address = gsub("III.", "", petitioner_counsel_address)) %>%
        mutate(petitioner_counsel_address = gsub("II", "", petitioner_counsel_address)) %>%
        mutate(petitioner_counsel_address = gsub("III", "", petitioner_counsel_address))
      extract_address <- function(address) {
        match <- regexpr("[a-zA-Z0-9]", address)
        if (match == -1) {
          return(address)
        } else {
          return(substr(address, match, nchar(address)))
        }
      } #Grab from first alpha-numeric character
      petitioner_counsel$petitioner_counsel_address <- sapply(petitioner_counsel$petitioner_counsel_address, function(x) {
        x <- iconv(x, to = "UTF-8")
        extract_address(x)
      })
      # Apply the function to the petitioner_counsel_address column
      petitioner_counsel$petitioner_counsel_address <- sapply(petitioner_counsel$petitioner_counsel_address, extract_address)

      petitioner_counsel <- petitioner_counsel %>%
        mutate(petitioner_counsel_fix = case_when(
          grepl("Law Offices of", petitioner_counsel_address, ignore.case = T) ~ "Law Offices of",
          grepl("Law Office of", petitioner_counsel_address, ignore.case = T) ~ "Law Office of",
          grepl("Law Group", petitioner_counsel_address, ignore.case = T) ~ "Law Group",
          grepl("Associates", petitioner_counsel_address, ignore.case = T) ~ "Associates"))

      petitioner_counsel$petitioner_counsel_address = ifelse(!is.na(petitioner_counsel$petitioner_counsel_fix), apply(petitioner_counsel, 1, function(x){
        gsub(x["petitioner_counsel_fix"], "", x["petitioner_counsel_address"])}), petitioner_counsel$petitioner_counsel_address)


      petitioner_counsel <- petitioner_counsel %>%
        mutate(petitioner_counsel_address = case_when(
          is.na(petitioner_counsel_fix) ~ petitioner_counsel_address,
          petitioner_counsel_fix == "Law Offices of" ~ paste0(petitioner_counsel_fix, " ", petitioner_counsel_truncated, petitioner_counsel_address),
          petitioner_counsel_fix == "Law Office of" ~ paste0(petitioner_counsel_fix, " ", petitioner_counsel_truncated, petitioner_counsel_address),
          petitioner_counsel_fix == "Law Group" ~ paste0(petitioner_counsel_truncated, " ", petitioner_counsel_fix, petitioner_counsel_address),
          petitioner_counsel_fix == "Associates" ~ paste0(petitioner_counsel_truncated, " &", petitioner_counsel_fix, petitioner_counsel_address),
        )) %>%
        select(-c(petitioner_counsel_fix))


      petitioner_counsel <- petitioner_counsel %>%
        mutate(petitioner_counsel_address = mapply(function(truncated, address) {
          gsub(truncated, "", address)
        }, petitioner_counsel_truncated, petitioner_counsel_address))













    } #Petitioner Counsel Parse
    {
      respondent_counsel <- data.frame(docket_entries$respondent_counsel)
      names(respondent_counsel)[1] <- "respondent_counsel"
      respondent_counsel$respondent_counsel <- gsub(".*\\: ", "", respondent_counsel$respondent_counsel)
      remove_text_after_third_space <- function(x) {
        # Split the text string into separate words
        words <- strsplit(x, " ")[[1]]

        # Remove any words beyond the third word
        truncated_words <- words[1:3]

        # Combine the truncated words back into a single string
        truncated_string <- paste(truncated_words, collapse = " ")

        # Return the truncated string
        return(truncated_string)
      } #Function to Trim respondent Counesl Name
      respondent_counsel$respondent_counsel_truncated <- sapply(respondent_counsel$respondent_counsel, remove_text_after_third_space) #Remove All Text After Third Space (Captures Most Names Re: First - Middle - Last)
      respondent_counsel$respondent_counsel_truncated <- gsub("POB", "", respondent_counsel$respondent_counsel_truncated )    #Remove any "PO" or "P.O"
      respondent_counsel$respondent_counsel_truncated <- gsub("P.O", "", respondent_counsel$respondent_counsel_truncated )    #Remove any "PO" or "P.O"
      respondent_counsel$respondent_counsel_truncated <- gsub("PO", "", respondent_counsel$respondent_counsel_truncated )    #Remove any "PO" or "P.O"
      respondent_counsel$respondent_counsel_truncated <- gsub("[[:digit:]].*", "", respondent_counsel$respondent_counsel_truncated )    #Remove Any Numbers
      respondent_counsel$respondent_counsel_truncated <- gsub("\\,", "", respondent_counsel$respondent_counsel_truncated )    #Remove Any Numbers
      respondent_counsel$respondent_counsel_truncated <- trimws(respondent_counsel$respondent_counsel_truncated)
      #Trim WS
      respondent_counsel$respondent_counsel_truncated <- gsub(" The", "", respondent_counsel$respondent_counsel_truncated )    #Remove any "The *Lawfirm*"
      respondent_counsel$respondent_counsel_truncated <- gsub("Univ.*", "", respondent_counsel$respondent_counsel_truncated )    #Remove any University
      respondent_counsel$respondent_counsel_truncated <- gsub(" \\..*", "", respondent_counsel$respondent_counsel_truncated )    #Remove trailing periods
      respondent_counsel$respondent_counsel_truncated <- ifelse(grepl("NA NA", respondent_counsel$respondent_counsel_truncated), "", respondent_counsel$respondent_counsel_truncated)

      respondent_counsel$respondent_counsel_address <- respondent_counsel$respondent_counsel

      respondent_counsel$respondent_counsel_address <- trimws(respondent_counsel$respondent_counsel_address)
      respondent_counsel$respondent_counsel_address <- sub("^,\\s*", "", respondent_counsel$respondent_counsel_address)

      respondent_counsel <- respondent_counsel %>%
        mutate(respondent_counsel_truncated = ifelse(grepl("Jr.", respondent_counsel_address), paste0(respondent_counsel_truncated, " Jr."), respondent_counsel_truncated)) %>%
        mutate(respondent_counsel_truncated = ifelse(grepl("Sr.", respondent_counsel_address), paste0(respondent_counsel_truncated, " Sr."), respondent_counsel_truncated)) %>%
        mutate(respondent_counsel_truncated = ifelse(grepl("II", respondent_counsel_address), paste0(respondent_counsel_truncated, " II"), respondent_counsel_truncated)) %>%
        mutate(respondent_counsel_truncated = ifelse(grepl("III", respondent_counsel_address) & !grepl("II", respondent_counsel_truncated), paste0(respondent_counsel_truncated, " III"), respondent_counsel_truncated)) %>%
        mutate(respondent_counsel_address = gsub("Jr.", "", respondent_counsel_address)) %>%
        mutate(respondent_counsel_address = gsub("Sr.", "", respondent_counsel_address)) %>%
        mutate(respondent_counsel_address = gsub("II.", "", respondent_counsel_address)) %>%
        mutate(respondent_counsel_address = gsub("III.", "", respondent_counsel_address)) %>%
        mutate(respondent_counsel_address = gsub("II", "", respondent_counsel_address)) %>%
        mutate(respondent_counsel_address = gsub("III", "", respondent_counsel_address))
      extract_address <- function(address) {
        match <- regexpr("[a-zA-Z0-9]", address)
        if (match == -1) {
          return(address)
        } else {
          return(substr(address, match, nchar(address)))
        }
      }
      respondent_counsel$respondent_counsel_address <- sapply(respondent_counsel$respondent_counsel_address, function(x) {
        x <- iconv(x, to = "UTF-8")
        extract_address(x)
      })
      # Apply the function to the respondent_counsel_address column
      respondent_counsel$respondent_counsel_address <- sapply(respondent_counsel$respondent_counsel_address, extract_address)

      # respondent_counsel$name_count<- sapply(1:nrow(respondent_counsel), function(x) str_count(respondent_counsel$respondent_counsel[x], respondent_counsel$respondent_counsel_truncated[x]))

      respondent_counsel <- respondent_counsel %>%
        mutate(respondent_counsel_fix = case_when(
          grepl("Law Offices of", respondent_counsel_address, ignore.case = T) ~ "Law Offices of",
          grepl("Law Office of", respondent_counsel_address, ignore.case = T) ~ "Law Office of",
          grepl("Law Group", respondent_counsel_address, ignore.case = T) ~ "Law Group",
          grepl("Associates", respondent_counsel_address, ignore.case = T) ~ "Associates"))

      respondent_counsel$respondent_counsel_address = ifelse(!is.na(respondent_counsel$respondent_counsel_fix), apply(respondent_counsel, 1, function(x){
        gsub(x["respondent_counsel_fix"], "", x["respondent_counsel_address"])}), respondent_counsel$respondent_counsel_address)


      respondent_counsel <- respondent_counsel %>%
        mutate(respondent_counsel_address = case_when(
          is.na(respondent_counsel_fix) ~ respondent_counsel_address,
          respondent_counsel_fix == "Law Offices of" ~ paste0(respondent_counsel_fix, " ", respondent_counsel_truncated, respondent_counsel_address),
          respondent_counsel_fix == "Law Office of" ~ paste0(respondent_counsel_fix, " ", respondent_counsel_truncated, respondent_counsel_address),
          respondent_counsel_fix == "Law Group" ~ paste0(respondent_counsel_truncated, " ", respondent_counsel_fix, respondent_counsel_address),
          respondent_counsel_fix == "Associates" ~ paste0(respondent_counsel_truncated, " &", respondent_counsel_fix, respondent_counsel_address),
        )) %>%
        select(-c(respondent_counsel_fix))

      respondent_counsel <- respondent_counsel %>%
        mutate(respondent_counsel_address = mapply(function(truncated, address) {
          gsub(truncated, "", address)
        }, respondent_counsel_truncated, respondent_counsel_address))



    } #Respondent Counsel Parse
    {

      docket_entries$petitioner_counsel_address <- petitioner_counsel$petitioner_counsel_address
      docket_entries$petitioner_counsel_address <- ifelse(is.na(docket_entries$petitioner_counsel_address), "", docket_entries$petitioner_counsel_address)
      docket_entries$petitioner_counsel <- petitioner_counsel$petitioner_counsel_truncated
      docket_entries$petitioner_counsel_address <- gsub(docket_entries$petitioner_counsel, "", docket_entries$petitioner_counsel_address)

      docket_entries$respondent_counsel_address <- respondent_counsel$respondent_counsel_address
      docket_entries$respondent_counsel_address <- ifelse(is.na(docket_entries$respondent_counsel_address), "", docket_entries$respondent_counsel_address)
      docket_entries$respondent_counsel <- respondent_counsel$respondent_counsel_truncated
      docket_entries$respondent_counsel_address <- gsub(docket_entries$respondent_counsel, "", docket_entries$respondent_counsel_address)

    } #Add Parsed & Cleaned Counsel
    {
      {
        for (i in 1:nrow(docket_entries)) {
          original_text <- docket_entries$text_original[i]

          for (month in months) {
            original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
          }

          docket_entries$submitted_to_check[i] <- original_text
        }

        split_rows <- strsplit(docket_entries$submitted_to_check, "\n###\n")
        filtered_rows <- lapply(split_rows, function(row) {
          has_submitted_to <- grepl("submitted to", row, ignore.case = TRUE)
          row[has_submitted_to]
        })
        cleaned_rows <- lapply(filtered_rows, function(row) {
          gsub("Justice ", "", row)
        })
        cleaned_rows <- lapply(cleaned_rows, function(row) {
          gsub(".*submitted to ", "", row, ignore.case = T)
        })
        cleaned_rows <- lapply(cleaned_rows, function(row) {
          gsub("\\..*", "", row, ignore.case = T)
        })
        cleaned_rows <- lapply(cleaned_rows, function(row) {
          gsub("\\. ", "\n###\n", row)
        })

        docket_entries$submitted_to <- cleaned_rows

        docket_entries <- docket_entries %>%
          mutate(submitted_to = sapply(submitted_to, paste, collapse = "; "))

        docket_entries$submitted_to <- ifelse(docket_entries$type == "Docketed Case", "", docket_entries$submitted_to)
      } #Submitted To
      {
        docket_entries$referred_to_court <- ifelse(grepl("referred to the Court", docket_entries$text_original, ignore.case = T), "Yes", "No")
        docket_entries$referred_to_court <- ifelse(docket_entries$type == "Docketed Case", "", docket_entries$referred_to_court)
      } #Referred to Court
      {
        for (i in 1:nrow(docket_entries)) {
          original_text <- docket_entries$text_original[i]

          for (month in months) {
            original_text <- gsub(paste0("\\b", month), paste0("\n###\n", month), original_text)
          }

          docket_entries$application_type_check[i] <- original_text
        }

        split_rows <- strsplit(docket_entries$application_type_check, "\n###\n")
        filtered_rows <- lapply(split_rows, function(row) {
          has_application_type <- grepl(", submitted to", row, ignore.case = TRUE)
          row[has_application_type]
        })

        cleaned_rows <- lapply(filtered_rows, function(row) {
          gsub("\\([^()]*\\)", "", row)
        })
        cleaned_rows <- lapply(cleaned_rows, function(row) {
          trimws(row)
        })
        cleaned_rows <- lapply(cleaned_rows, function(row) {
          gsub(".*for ", "", row, ignore.case = )
        })
        cleaned_rows <- lapply(cleaned_rows, function(row) {
          gsub("\\,.*", "", row)
        })
        cleaned_rows <- lapply(cleaned_rows, function(row) {
          gsub("a ", "", row)
        })

        docket_entries$application_type = cleaned_rows
        docket_entries$application_type = ifelse(docket_entries$type == "Docketed Case", "", docket_entries$application_type)
        docket_entries$application_type = str_to_title(docket_entries$application_type)


      } #Application Type



    } #Special Application Terms
    {

      docket_entries <- docket_entries %>%
        mutate(docket_number = gsub("No. ", "", docket_number)) %>%
        mutate(filing_type = file_type) %>%
        mutate(petitioner_counsel = gsub("[^[:alpha:].\\s ]+", "", petitioner_counsel)) %>%
        mutate(respondent_counsel = gsub("[^[:alpha:].\\s ]+", "", respondent_counsel)) %>%
        mutate(petition_type = type) %>%
        mutate(most_recent_order = ifelse(grepl("SET FOR ARGUMENT", text_original, ignore.case = TRUE), "SET FOR ARGUMENT", NA)) %>%
        mutate(most_recent_order = ifelse(grepl("Argued. ", text_original, ignore.case = TRUE), "ARGUED", most_recent_order)) %>%
        mutate(most_recent_order = ifelse(grepl("ISSUED", text_original, ignore.case = TRUE), "JUDGEMENT ISSUED", most_recent_order)) %>%
        mutate(most_recent_order = ifelse(is.na(most_recent_order), paste0(petition_type, " ", certiorari), most_recent_order)) %>%
        mutate(most_recent_order = ifelse(is.na(most_recent_order), paste0(petition_type, " ", certiorari), most_recent_order)) %>%
        mutate(petitioner_address_fix = gsub("Jr\\.|Sr\\.|II|III", "", petitioner_counsel),
               respondent_address_fix = gsub("Jr\\.|Sr\\.|II|III", "", respondent_counsel)) %>%
        mutate(petitioner_address_fix = trimws(petitioner_address_fix),
               respondent_address_fix = trimws(respondent_address_fix)) %>%
        mutate(petitioner_counsel_address = gsub(petitioner_address_fix, "", petitioner_counsel_address),
               respondent_counsel_address = gsub(respondent_address_fix, "", respondent_counsel_address)) %>%
        mutate(petitioner_counsel_address = trimws(petitioner_counsel_address),
               respondent_counsel_address = trimws(respondent_counsel_address)) %>%
        mutate(amicus_indicator = ifelse(amicus_indicator == 1, "Yes", "No")) %>%
        mutate(first_conference = conference_date) %>%
        select(docket_number, petition_type, petitioner, petitioner_counsel, petitioner_counsel_address, respondent, respondent_counsel, respondent_counsel_address, docketed, submitted_to, referred_to_court, application_type, linked_with, lower_court, lower_court_case_number, lower_court_decision_date, lower_court_rehearing_denied, amicus_indicator, amicus_filers, amicus_count, first_conference, conference_count, multiple_conference_dates, most_recent_order, majority_opinion_writer, opinion_type, number_of_opinions, opinions_by_type, opinion_filings, argument_date, special_filing, rehearing_filed, rehearing_order, docket_url)

      chr_cols <- names(docket_entries)[sapply(docket_entries, is.character)]
      for (col in chr_cols) {
        if (any(sapply(docket_entries[[col]], inherits, "raw"))) {
          docket_entries[[col]] <- iconv(docket_entries[[col]], from = "ISO-8859-1", to = "UTF-8")
        } else {
          docket_entries[[col]] <- iconv(docket_entries[[col]], to = "UTF-8")
        }
      }

    } #Final Cleaning (Arrange columns & convert bytes to UTF-8)

  } #Cleaning


return(docket_entries)

  } #Parse Individual Docket Entries

docket_call <- function(urls, rate, sleep) {
  docket_frame <- data.frame(url = character(), text = character(), stringsAsFactors = FALSE)

  for (i in seq(1, length(urls), by = rate)) {
    batch_urls <- urls[i:min(i+rate-1, length(urls))]
    for (j in seq_along(batch_urls)) {
      url <- batch_urls[j]
      tryCatch({
        text <- gettxt(url, encoding = "UTF-8")
        docket_frame <- rbind(docket_frame, data.frame(url = url, text = text, stringsAsFactors = FALSE))
      }, error = function(e) {
        cat(paste("Error occurred with url:", url, "\n"))
        idx <- which(urls == url)
        # subset the urls vector from that point
        urls <- urls[(idx+1):length(urls)]
      })
    }
    if (i+rate-1 < length(urls)) {
      cat("I Don't Feel So Good...\n...\n...\nMr. Stark?\n...\n...\n...\nI Don't Wanna Go...\n\nJust Kidding - Taking a break\n")
      Sys.sleep(sleep)
    }
  }

  return(docket_frame)
} #Call to Docket via Internet

include_func <- function(docket_entities, cols){
  if (!is.null(cols)) {
    docket_entities <- docket_entities %>%
      select(all_of(cols))
  }
  return(docket_entities)
} #Include Parameter

exclude_func <- function(docket_entities, cols){
  if (!is.null(cols)) {
    docket_entities <- docket_entities %>%
      select(-cols)
  }
  return(docket_entities)
} #Exclude Parameter

write_csv_func <- function(docket_entries, write_csv) {
  if (write_csv) {
    cat("Code to Save Dataframe as (.csv):\n")
    cat("library(utils)\n")
    cat("write.csv(<SEARCH QUERY OBJECT NAME>, file = '<SAVE FILE>.csv', row.names = FALSE)\n")
  }
}

write_xlsx_func <- function(docket_entries, write_xlsx) {
  if (write_xlsx) {
    cat("Code to Save Dataframe as (.xlsx):\n")
    cat("library(writexl)\n")
    cat("write_xlsx(<SEARCH QUERY OBJECT NAME>, path = '<SAVE FILE>.xlsx')\n")
  }
}

write_reactable_func <- function(docket_entries, write_reactable){
  if (write_reactable){
    cat("Code to Create (.HTML) Table Using Reactable:\n")
    cat("library(reactable); library(reactablefmtr)\n")
    cat("reactable(docket_entries, searchable = T,\n defaultPageSize = 20,\n theme = fivethirtyeight(font_size = 12, font_color = 'grey',\n cell_padding = 6)) %>%\n")
    cat("add_title('<YOUR TITLE HERE>') %>%\n")
    cat("add_subtitle('<YOUR SUBTITLE HERE>')\n")
    }
}

docket_search <- function(docket_id, rate = 50, sleep = 30, include = NULL, exclude = NULL, write_csv = FALSE, write_xlsx = FALSE, write_reactable = FALSE) {
  urls <- suppressWarnings(process_docket_id(docket_id))
  urls <- gsub(" ", "", urls)
  urls <- gsub("- ", "-", urls)
  urls <- gsub(" -", "-", urls)

  docket_frame <- docket_call(urls, rate, sleep)

  docket_frame$text <- gsub("\\xe2\\x80\\xa2", " ", docket_frame$text)
  docket_frame$text <- trimws(docket_frame$text)
  docket_entities <- suppressWarnings(clean_docket_frame(docket_frame = docket_frame))

  if (!is.null(include)) {
    docket_entities <- include_func(docket_entities, include)
  }

  if (!is.null(exclude)) {
    docket_entities <- exclude_func(docket_entities, exclude)
  }

  write_csv_func(docket_entities, write_csv)
  write_xlsx_func(docket_entities, write_xlsx)
  write_reactable_func(docket_entries, write_reactable)

  return(docket_entities)

} # Primary Docket Search

print_flattened_list <- function(column) {
  flattened_list <- unlist(lapply(column, function(x) strsplit(x, "; ")[[1]]))
  print(flattened_list)
}

```

## **docket_search()**

`docket_search`serves as an automated tool for collecting, parsing, and cleaning information from docketed cases, petitions, and motions to the United States Supreme Court. Implementation of `docket_search` requires providing a docket number corresponding to the petition (or application/motion) of interest as a character vector. The function call will also accept a list of docket numbers, as well as an object containing a list of comma-separated character vectors. For more information on the Supreme Court docket, *see*   [supremecourt.gov](https://www.supremecourt.gov/docket/docket.aspx).


## **Function Description**

The `docket_search` function takes several arguments to customize search queries:

- `docket_id`: The docket number of interest - written as a character vector in **R**. This can take the form of filed petitions (e.g., "19-1392"), applications (e.g., "22A948"), or motions (e.g., "22M11"). 

*Note*: The function will also accept list objects containing comma-separated character vectors of docket numbers (e.g., docket_ids <- c("19-108", "19-184", "19-199", "19-251"). 

*Further*: The function will accept petitions filed pursuant to the Court's **original** jurisdiction, though it is recommended that docket numbers be written in the style similar to supremecourt.gov (e.g., "22O145").

- `rate`: The number of requests to process per function call (default is **50**). Long, repeated calls to supremecourt.gov can produce SSL errors. Limiting the `rate` of docket queries deters incidental SSL errors, though the package is built to adapt and continue following these errors while indicating which docket filings (if any) were unsuccessfully retrieved. The function will allow up to 5 url-specific errors or 20 total errors before ending the function. Based on prior testing, an SSL error tends to yield every 4,000 to 5,000 requests.  
- `sleep`: The number of seconds to wait between docket requests (default is **30**).
- `include`: A character vector that will limit the output variables to only those requested (default is **NULL**).
- `exclude`: A character vector that will exclude any output variables requested (default is **NULL**)
- `write_csv`: Logical value indicating whether to print code to convert the output dataframe to a .csv file (default is **FALSE**).
- `write_xlsx`: Logical value indicating whether to print code to convert the output dataframe to an excel file (default is **FALSE**).
- `write_reactable`: Logical value indicating whether to print code to convert the output dataframe to a .html file using `reactable()` (default is **FALSE**).

## `docket_search` **Variables**

```{r, echo = F}
dobbs_test <- docket_search(docket_id = "19-1392")
names(dobbs_test)
```

- `docket_id`: The docket number corresponding with the search query. 
- `petition_type`: Factor term indicating *Docketed Petition*, *Application*, or *Motion*.
- `petitioner`: Petitioning party of interest.
- `petitioner_counsel`: Counsel of Record for petitioning party of interest. 
- `petitioner_counsel_address`: Listed address of Counsel of Record for petitioning party of interest. 
- `respondent`: Responding party of interest.
- `respondent_counsel`: Counsel of Record for responding party of interest. 
- `respondent_counsel_address`: Listed address of Counsel of Record for responding party of interest. 
- `docketed`: Date the petition was docketed with the Court. 
- `submitted_to`: Denotes which Justice(s) an **Application** or **Motion** was submitted to.
- `referred_to_court``: Indicates whether the **Application** or **Motion** was referred to the full Court for consideration. 
- `application_type`: Indicates the specific relief sought by application (e.g., ***Stays***, ***Injunctions Pending Appeal***, etc.)
- `linked_with`: Indicates whether the docketed petition (or application/motion) is linked with any other docketed filings. 
- `lower_court`: The most recent lower court to take action prior to filing at SCOTUS. 
- `lower_court_case_number`: Docket number corresponding with the relevant filing of interest at the lower court. 
- `lower_court_decision_date`: Date corresponding with most recent action at lower court. 
- `lower_court_rehearing_denied`: Indicates whether a rehearing request was filed (and denied) at the relevant lower court. 
- `amicus_indicator`: Dichotomous term indicating whether any briefs were filed as amicus curiae. 
- `amicus_filers`: A nested list containing all amicus filers (if any).
- `amcius_count`: Integer representing the total number of amicus filings (if any).
- `first_conference`: Date indicating the first conference where the relevant petition was considered (**Petitions Only**). 
- `conference_count`: Integer representing the number of times the petition was re-listed and considered at another conference (**Petitions Only**). 
- `multiple_conference_dates`: Dichtomous term indicating whether the petition was considered at more than one conference (**Petitions Only**). 
- `most_recent_order`: Factor indicating the most recent action taken by Court (*Docketed*, ***Petition DENIED***, ***Petition GRANTED***, ***SET FOR ARGUMENT***, ***ARGUED***, ***JUDGEMENT ISSUED***).
- `majority_opinion_writer`: Character vector indicating justice who wrote majority opinion (**Argued and Decided Petitions Only**). 
- `opinion_type`: Factor term indicating disposition taken on petition (*DIG*, *AFFIRMED*, ***VACATED AND REMANDED***, ***REVERSED AND REMANDED***, ***No Opinion Issued***, ***GVR***).
- `number_of_filings`: Integer indicating the total number of opinions filed (***Majority Opinion*** plus any ***Concurrences*** and ***Dissents***).
- `opinions_by_type`: Nested list indicating the number of ***Concurrences*** and ***Dissents*** filed (if any). 
- `opinion_filings`: Nested list indicating which justice(s) filed each opinion. 
- `argument_date`: Date of oral argument (if any). 
- `special_filing`: Factor indicating whether filing considered writs of ***Habeas Corpus*** or ***Mandamus***, as well as whether it considered ***Capital Punishment*** (e.g., ***Stays of Execution***) or is a petition filed under the Court's ***Original Jurisdiction***.
- `rehearing_filed`: Dichotomous term noting whether a rehearing petition was filed. 
- `rehearing_order`: Order on rehearing petition (if any).
- `docket_url`: Http address corresponding with location of docket of interest on supremecourt.gov.

## **Example Walkthrough**

Here's an example of how to use the `docket_search` function using *Dobbs v. Jackson Women's Health Clinic* (2022), one of the largest docket sheets hosted by the Supreme Court:


```{r, eval = F}
#Load scotustext package
install.packages("scotustext")
library(scotustext)
```

```{r}
#Call to Docket Using Docket Number for Dobbs v. Jackson (19-1392)
dobbs_test <- docket_search(docket_id = "19-1392")
```

**Note**: *amicus_filers*, *multiple_conference_dates*, *number_of_opinions*, and *opinion_filings* are all stored as flattended lists to allow for exporting to (.csv) and (.xlsx). However, these can be converted back to their original structure using the function below: 

```{r, eval = F}
print_flattened_list <- function(column) {
  if (length(column) > 1) {
    for (row in column) {
      if (length(row) > 0) {
        elements <- unlist(strsplit(row, "; "))
        print(list(elements))
      } else {
        print(list())
      }
    }
  } else {
    nested_list <- lapply(column[[1]], function(element) list(unlist(strsplit(element, "; "))))
    print(nested_list)
  }
}
print_flattened_list(<DOCKET OBJECT AND INDEX COLUMN>)
```

```{r}
#List of Conferences Where Dobbs Was Considered
print_flattened_list(dobbs_test$multiple_conference_dates)

#List of Opinions Filed
print_flattened_list(dobbs_test$opinion_filings)

#List of Amicus Filers
print_flattened_list(dobbs_test$amicus_filers)

```
